<!-- Dependencies: tidyverse, psych, common/pretty_table.R -->

Coren, S. (1995). Differences in Divergent Thinking as a Function of Handedness and Sex. The American Journal of Psychology, 108(3), 311. https://doi.org/10.2307/1422892

The AUT was scored only on fluency, the number of responses that each person came up with:

"n, divergent thinking measures have been presumed to be
 measures of creativity. One of the most popular of these tests is the Alternate
 Uses Test, where subjects are required to find novel uses for common objects.
 The variant used in this study was Form A (Christensen, Guilford, Merrifield,
 & Wilson, 1960). It consists of three parts, each of which contains three
 common items (e.g., a shoe) and space for up to six alternative uses per
 item. Each part is timed at 4 min. The score is simply the number of novel
 uses for each item that the participant generates."

The Authors report means and SD for men and women, for each of four handedness groups. However, they do not report n for each group (except for men and women), which makes it impossible to aggregate means and SDs exactly.

For analysis, assume equal in each handedness group, and calculate overall means/SDs for right vs. left, strong vs. mixed handers.

### {.tabset}

```{r}
study <- "coren_1995"
task <- "AUT"
```
```{r}
handedness_measure <- "LPI"
es_type <- "d"
measure <- "Fluency"
```

```{r}
## Load data
input <- read_csv(here(extract_dir, "data", "input", "coren_1995_aut.csv"))
```

#### Assume equal n for each handedness group {.tabset}

Code assumed n for each handedness group.
```{r}
n_total <- 556
## Assuming equal n, each of the four handedness groups has 139
n_male <- 231
## Assuming equal n and rounding down, males have 57 in each group
## Assuming equal n, males have 58 in three goups, 57 in one
## I will assume that the strong left group has 57
n_female <- 325
## Assuming equal n and rounding down, females have 81 in each group
## Assuming equal n, females have 81 in three groups, 82 in one.
## I will assume that the strong right group has 82.

assume_n <- input %>%
  filter(handedness != "all") %>%
  mutate(n = case_when(
                       handedness == "strong_right" & sex == "m" ~ 58,
                       handedness == "mixed_right"  & sex == "m" ~ 58,
                       handedness == "mixed_left"   & sex == "m" ~ 58,
                       handedness == "strong_left"  & sex == "m" ~ 57,
                       handedness == "strong_right" & sex == "f" ~ 82,
                       handedness == "mixed_right"  & sex == "f" ~ 81,
                       handedness == "mixed_left"   & sex == "f" ~ 81,
                       handedness == "strong_left"  & sex == "f" ~ 81
                       )
)

## Review assumed n's
assume_n %>% pretty_table(title = str_c(study, ", ", task, ": assumed group Ns"))
```

Calculate group means, SDs, for each handedness group, collapsing across sex.
Store this data in a new table, and save to a file: "data/proc/...proc_1.csv"
```{r}

proc_1 <- tibble::tibble(n = numeric(),
                         handedness = factor(),
                         mean = numeric(),
                         sd = numeric()
                         )

## Define function to calculate stats for each handedness group, across sex
## Input: n, handedness group, input data for coren_1995_AUT
## Return: a tibble row with columns n, handedness, mean, sd
## Depends on: tibble, lib/util.R
stats_across_sex <- function(data, h_grp) {
  ## x1 is coded for males, x2 for females
  m1 <- data %>% filter(handedness == h_grp & sex == "m") %>% .[["mean"]]
  m2 <- data %>% filter(handedness == h_grp & sex == "f") %>% .[["mean"]]
  n1 <- data %>% filter(handedness == h_grp & sex == "m") %>% .[["n"]]
  n2 <- data %>% filter(handedness == h_grp & sex == "f") %>% .[["n"]]
  sd1 <- data %>% filter(handedness == h_grp & sex == "m") %>% .[["sd"]]
  sd2 <- data %>% filter(handedness == h_grp & sex == "f") %>% .[["sd"]]

  stats_row <- tibble::tibble(n = n1 + n2,
                     handedness = h_grp,
                     mean = agg_mean_cochrane(m1 = m1, m2 = m2, n1 = n1, n2 = n2),
                     sd = agg_sd_cochrane(m1 = m1, m2 = m2, n1 = n1, n2 = n2,
                                           sd1 = sd1, sd2 = sd2)
                     )

  return(stats_row)
}

h_grps <- unique(assume_n[["handedness"]])
for (j in 1:length(h_grps)) {
  stats_row <- stats_across_sex(assume_n, h_grps[[j]])
  proc_1 <- proc_1 %>% add_row(stats_row)
}

write_csv(proc_1, here(extract_dir, "data", "proc", str_c(study, "_", task, "_proc_1.csv")))

## Review calculated group means, SDs
proc_1 %>% pretty_table(title = str_c(study, ", ", task, ": calculated group stats (all 4 groups)"))
```

```{r}
## Define function to calculate stats across handedness groups
## Input: proc_1, handedness groups to collapse, label for new group
## Return: a tibble row with columns n, handedness, mean, sd
## Depends on: tibble, lib/util.R
stats_across_h_grps <- function(proc_1, h_grps, h_grp_new) {

  n1 <- proc_1 %>% filter(handedness == h_grps[[1]]) %>% .[["n"]]
  n2 <- proc_1 %>% filter(handedness == h_grps[[2]]) %>% .[["n"]]
  m1 <- proc_1 %>% filter(handedness == h_grps[[1]]) %>% .[["mean"]]
  m2 <- proc_1 %>% filter(handedness == h_grps[[2]]) %>% .[["mean"]]
  sd1 <- proc_1 %>% filter(handedness == h_grps[[1]]) %>% .[["sd"]]
  sd2 <- proc_1 %>% filter(handedness == h_grps[[2]]) %>% .[["sd"]]

  stats_row <- tibble::tibble(n = n1 + n2,
                          handedness = h_grp_new,
                          mean = agg_mean_cochrane(m1 = m1, m2 = m2, n1 = n1, n2 = n2),
                          sd = agg_sd_cochrane(m1 = m1, m2 = m2, n1 = n1, n2 = n2,
                                               sd1 = sd1, sd2 = sd2)
  )
  return(stats_row)
}
```

#### Right/left

Calculate group means, SDs for Right vs. Left handers.
(Right vs. left means strong right, mixed right vs. strong left, mixed left)
Save results to file: "data/proc/...proc_2_rl.csv"
```{r}
proc_2_rl <- tibble::tibble(n = numeric(),
                         handedness = factor(),
                         mean = numeric(),
                         sd = numeric()
                         )


h_grps <- c("strong_right", "mixed_right")
h_grp_new <- "right"
proc_2_rl <- proc_2_rl %>%
  add_row(stats_across_h_grps(proc_1, h_grps, h_grp_new))

h_grps <- c("strong_left", "mixed_left")
h_grp_new <- "left"
proc_2_rl <- proc_2_rl %>%
  add_row(stats_across_h_grps(proc_1, h_grps, h_grp_new))

write_csv(proc_2_rl, here(extract_dir, "data", "proc", str_c(study, "_", task, "_proc_2_rl.csv")))

## Review calculated group means, SDs
proc_2_rl %>% pretty_table(title = str_c(study, ", ", task, ": calculated group stats (right/left)"))
```

Find and report effect size.
```{r}
n1 <- proc_2_rl %>% filter(handedness == "right")  %>% .[["n"]]
n2 <- proc_2_rl %>% filter(handedness == "left")  %>% .[["n"]]
m1 <- proc_2_rl %>% filter(handedness == "right")  %>% .[["mean"]]
m2 <- proc_2_rl %>% filter(handedness == "left")  %>% .[["mean"]]
sd1 <- proc_2_rl %>% filter(handedness == "right")  %>% .[["sd"]]
sd2 <- proc_2_rl %>% filter(handedness == "left")  %>% .[["sd"]]

d <- msd_to_d(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2)

esci <- psych::cohen.d.ci(d = d, n1 = n1, n2 = n2, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          h = handedness_measure, rl_sm = "R/L",
          n1 = n1, n2 = n2,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          notes = "From Ms, SDs, approx Ns (Agg.)", include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure, " (right/left)"))
```

#### Strong/mixed

Calculate group means, SDs for Strong vs. Mixed handers.
(Strong vs. mixed means strong right, strong left vs. mixed right, mixed left)
Save results to file: "data/proc/...proc_2_sm.csv"

```{r}
proc_2_sm <- tibble::tibble(n = numeric(),
                         handedness = factor(),
                         mean = numeric(),
                         sd = numeric()
                         )


h_grps <- c("strong_right", "strong_left")
h_grp_new <- "strong"
proc_2_sm <- proc_2_sm %>%
  add_row(stats_across_h_grps(proc_1, h_grps, h_grp_new))

h_grps <- c("mixed_right", "mixed_left")
h_grp_new <- "mixed"
proc_2_sm <- proc_2_sm %>%
  add_row(stats_across_h_grps(proc_1, h_grps, h_grp_new))

write_csv(proc_2_sm, here(extract_dir, "data", "proc", str_c(study, "_", task, "_proc_2_sm.csv")))

## Review calculated group means, SDs
proc_2_sm %>% pretty_table(title = str_c(study, ", ", task, ": calculated group stats (strong/mixed)"))
```

Find and report effect size.
```{r}
n1 <- proc_2_sm %>% filter(handedness == "strong")  %>% .[["n"]]
n2 <- proc_2_sm %>% filter(handedness == "mixed")  %>% .[["n"]]
m1 <- proc_2_sm %>% filter(handedness == "strong")  %>% .[["mean"]]
m2 <- proc_2_sm %>% filter(handedness == "mixed")  %>% .[["mean"]]
sd1 <- proc_2_sm %>% filter(handedness == "strong")  %>% .[["sd"]]
sd2 <- proc_2_sm %>% filter(handedness == "mixed")  %>% .[["sd"]]



d <- msd_to_d(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2)

esci <- psych::cohen.d.ci(d = d, n1 = n1, n2 = n2, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          h = handedness_measure, rl_sm = "S/M",
          n1 = n1, n2 = n2,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          notes = "From Ms, SDs, approx Ns (Agg.)", include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure, " (strong/mixed)"))
```
