<!-- Dependencies: tidyverse, psych, common/pretty_table.R -->

Feen, F. E., Zickert, N., Groothuis, T. G. G., & Geuze, R. H. (2020). Does hand skill asymmetry relate to creativity, developmental and health issues and aggression as markers of fitness? Laterality, 25(1), 53–86. https://doi.org/10.1080/1357650X.2019.1619750

For the AUT, subjects were all asked: "Within two minutes, enter as many uses for a book that you can think of."

Fluency: the number of valid answers.

"Combined" (In Zickert et al. 2019, this is called "Originality"): unique answers were divided into ten bins, from the 10% most common to the 10% least common. Each answer received an integer score from 1 (most common) to 10 (least common/most original). These were summed for each person.

"Originality" divide originality score by the number of valid answers. (As described in the main text, this variable was called "Originality/fluency" in Zickert et al., 2019).

From the main text: "Finally, we calculated three divergent thinking scores per participant: a fluency score, which was the amount of valid answers given; a combined score, which was the sum of the originality scores; and an originality score, which was the average originality score per valid answer. The details of the calculation and analysis can be found in Appendix 3."
Appendix 3 contradicts the main text as to how the AUT scores are named: "...for each participant we calculated the individual fluency score by counting the number of valid answers and the originality score by adding the creativity scores of the valid answers."
For analysis, I assume that the "combined" score represents Originality (sum)/Fluency, following the appendix.

The authors report inferential stats for each score, and for principle components, one of which included: Originality, Fluency, Combined, and something called "Artistic--questionnaire", which was different from "Artistic--self assessment." I infer that "Artistic--self assessment" was the slider scale response to the question "How artistically creative are you?"
Zickert et al., 2019 explain two Artistic creativity scores:
1. "Artistic creativity self-assessment": ???
1. "Artistic creativity score": sum of likert responses to how often participants do different creative activites. [0 - 30]

For each AUT score, the authors report an F-test, a p-value, and a beta value, as well as an Overall R^2, for a model including five regressors: Asymmetry score, Asymmetry score squared, Sex, Age, and Age squared. (Table 4) For meta-analysis, the beta coefficients for Originality, Fluency, and "Combined" are extracted (because the beta coefficient is from a mixed model, it cannot be pooled with other studies).


### {.tabset}

```{r}
study <- "feen_2020"
task <- "AUT"
```

```{r}
handedness_measure <- "Tap asym."
rl_sm <- "R/L"
```

```{r}
## N for fluency, originality, and combined
n <- 8353
```

#### Model R2 -> rho (probably innapropriate)
```{r}
es_type <- "model_rho"
```

```{r}
measure <- "Fluency"
model_r2 <- 0.049

## Use MBESS::ci.R to find CI for model R2 -> rho
## The model includes 5 regressors
rho_p <- r2_to_rho(model_r2, sign = "pos")
esci <- rho_p_ci(rho_p, N = n, K = 5, conf.level = 0.95)

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, effect = esci$effect, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From n, Model R2 (probably innapropriate) (zAi, zAi^2, sex, age, age^2)",
          include = 0
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
```{r}
measure <- "Originality" ## Using the name from Zickert et al., 2019 instead of "Combined"
model_r2 <- 0.040

rho_p <- r2_to_rho(model_r2, sign = "pos")
esci <- rho_p_ci(rho_p, N = n, K = 5, conf.level = 0.95)

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, effect = esci$effect, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From n, Model R2 (probably innapropriate) (zAi, zAi^2, sex, age, age^2)",
          include = 0
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
```{r}
measure <- "Originality/Fluency" ## Using the name from Zickert et al., 2019 instead of "Originality"
model_r2 <- 0.020

rho_p <- r2_to_rho(model_r2, sign = "pos")
esci <- rho_p_ci(rho_p, N = n, K = 5, conf.level = 0.95)

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, effect = esci$effect, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From n, Model R2 (probably innapropriate) (zAi, zAi^2, sex, age, age^2)",
          include = 0
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

#### Beta regression coeffients
```{r}
es_type <- "beta"
```

```{r}
measure <- "Fluency"
beta <- .305
p <- .0001 ## this is an upper bound on p -- CI calculated from this will be a conservative (wide) estimate

esci <- p_to_ci(p, beta)
es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, effect = esci$effect, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From β, n (zAi, zAi^2, sex, age, age^2)",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
```{r}
measure <- "Originality" ## Using the name from Zickert et al., 2019 instead of "Combined" - I think this is described backwards in Feen et al.'s main text, but labelled correctly in the table.
beta <- 1.424
p <- .0001 ## this is an upper bound on p -- CI calculated from this will be a conservative (wide) estimate

esci <- p_to_ci(p, beta)
es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, effect = esci$effect, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From β, n (zAi, zAi^2, sex, age, age^2)",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
```{r}
measure <- "Originality/Fluency" ## Using the name from Zickert et al., 2019 instead of "Originality"
beta <- 0.052
p <- .0001 ## this is an upper bound on p -- CI calculated from this will be a conservative (wide) estimate

esci <- p_to_ci(p, beta)
es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, effect = esci$effect, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From β, n (zAi, zAi^2, sex, age, age^2)",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
