<!-- Dependencies: tidyverse, psych, common/pretty_table.R -->

Felton, A. (2017). Interhemispheric Interaction and Creativity. [PhD Dissertation]

Group means and SDs are reported for strong and mixed handers, defined by a median split on the absolute value of EHI handedness (70 in each group, based on df = 140 for two-sample t-test).

For percent correct ("Accuracy"), reported numbers do not add up. Based on the means and SDs, there is a large, significant mixedy advantage (t = 3.8). But, the authors report a low t-value, 0.45. (And, SDs are extremely tight, compared to other RAT studies with similar sample size. For example, see Turner 2016). Could there be a typo in the table? I believe that most likely explanation is that the author accidentally presented SEM instead of SD: assuming this and calculating the true SD yields the reported t-value of 0.45.

```{r}
study <- "felton_2017"
task <- "RAT"
```

```{r}
handedness_measure <- "EHI"
rl_sm <- "S/M"
es_type = "d"
```

```{r}
measure <- "Problems solved out of 21"

## The authors seem to have accidentally reported SEM instead of SD.
## To recover the SD, I will multiply "SEM" by sqrt(n)

m_strong <- 56.09
reported_sd_strong <- 1.90
n_strong <- 71
sd_strong <- reported_sd_strong * sqrt(n_strong)
## Assuming the reported SEM, the actual SD is 16.01

m_mixed <- 57.34
reported_sd_mixed <- 2.01
n_mixed <- 71
sd_mixed <- reported_sd_mixed * sqrt(n_mixed)
## Assuming authors reported SEM, the actual SD is 16.94

d <- msd_to_d(m1 = m_strong, sd1 = sd_strong,
              m2 = m_mixed, sd2 = sd_mixed)

esci <- psych::cohen.d.ci(d = d, n1 = n_strong, n2 = n_mixed, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, inferred SDs, Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
```{r}
measure <- "Reaction time"

m_strong <- 5449
sd_strong <- 1035
n_strong <- 71

m_mixed <- 5447
sd_mixed <- 1451
n_mixed <- 71

d <- msd_to_d(m1 = m_strong, sd1 = sd_strong,
              m2 = m_mixed, sd2 = sd_mixed)

esci <- psych::cohen.d.ci(d = d, n1 = n_strong, n2 = n_mixed, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
