<!-- Dependencies: tidyverse, psych, common/pretty_table.R -->

Hattie, J., & Fitzgerald, D. (1983). Abstract: Do Left-Handers Tend to Be More Creative? The Journal of Creative Behavior, 17(4), 269–269. https://doi.org/10.1002/j.2162-6057.1983.tb00363.x

The authors replicated Katz 1980 with a sample of 103 18-year-olds, with handedness measured by the EHI using Oldfield's formula: R-L/R+L.

They report
- "The three handedness groups did not differ on any of the
measures of creativity." (No relevant stats reported)
- Correlation estimates (Pearson's rho) for TTCT-V (3 measures) and TTCT-F (4 measures)
- Correlation estimate (Pearson's rho) for the RAT)


```{r}
study <- "hattie_1983"
task <- "RAT"
```

```{r}
handedness_measure <- "EHI"
rl_sm <- "R/L"
```

### Pearson's ρ
```{r}
es_type <- "rho"
```

```{r}
## Load data
input_filename <- "hattie_1983_rat.csv"
input_path <- here(extract_dir, "data", "input", input_filename)
input <- read_csv(input_path)
## Display data
pretty_table(input, title = input_filename)
```

```{r}
## Get n from input file
## (because n is the same for all measures)
unique_n <- input %>% .[["n"]] %>% unique()
unique_n
if (length(unique_n == 1)) {
  n <- unique_n %>% first()
} else {
  stop(str_c(study, ", ", task,
    ": unexpected multiple values for n (total) in input file"))
}

str_c("n (total): ", n)
```

```{r}
measure <- "Problems solved out of 30 in 40 minutes"
rho <- input %>% filter(rat_measure == measure) %>% .[["rho"]]
esci <- rho_ci(rho, n, alpha = 0.05)

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, effect = esci$rho, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From rho, n", include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

### Cohen's D
The authors reported that "The three handedness groups did not differ on any of the
measures of creativity." (No relevant stats reported).

```{r}
es_type <- "d"
```

```{r}
## Get n for each group from input file
## (because n is the same for all measures)
n_input <- data.frame(n_right = NA, n_left = NA)
for (h in c("n_right", "n_left")) {
  unique_n <- input %>% .[[h]] %>% unique()
  if (length(unique_n == 1)) {
    n_input[[h]]  <- unique_n %>% first()
    n_input
  } else {
    stop(str_c(study, ", ", task,
      ": unexpected multiple values for n (right handers) in input file"))
  }
}

n_right <- n_input$n_right
n_left <- n_input$n_left
str_c(n_right, ", ", n_left)
```

```{r}
measure <- "Problems solved out of 30 in 40 minutes"
esci <- tibble(lower = NA, upper = NA, effect = NA)
es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n1 = n_right, n2 = n_left,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "Only 'no significant effect'",
          include = 1
  )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
