<!-- Dependencies: tidyverse, psych, common/pretty_table.R -->

Newland, G. A. (1981). Differences between Left- and Right-Handers on a Measure of Creativity. Perceptual and Motor Skills, 53(3), 787–792. https://doi.org/10.2466/pms.1981.53.3.787

Table 1 reports means, SDs, and Ns for right and left handers on Fluency, Flexibility, Originality, and Elaboration.

TTCT scores:
"The Torrance Tests of Creative Thinking (Torrance, 1974), Figural
Form B, was used to measure creativity. This three-part test of picrure con-
struction is scored on four subscales of Fluency, Flexibility, Originality, and
Elaboration. The tests were scored by a trained rater who was unaware of the
subjects' handedness."

```{r}
study <- "newland_1981"
task <- "TTCT(F)"
```
```{r}
handedness_measure <- "BNHI"
rl_sm <- "R/L"
es_type <- "d"
```

```{r}
## Load data
input_filename <- "newland_1981_ttct-f.csv"
input_path <- here(extract_dir, "data", "input", input_filename)
input <- read_csv(input_path)
## Display data
pretty_table(input, title = input_filename)
```

```{r}
n_right <- 96
n_left <- 96
```

```{r}
measure <- "Fluency"
m1 <- input %>%
  filter(handedness == "right" & ttct_measure == measure) %>%
  .[["mean"]]
m2 <- input %>%
  filter(handedness == "left" & ttct_measure == measure) %>%
  .[["mean"]]
sd1 <- input %>%
  filter(handedness == "right" & ttct_measure == measure) %>%
  .[["sd"]]
sd2 <- input %>%
  filter(handedness == "left" & ttct_measure == measure) %>%
  .[["sd"]]

d <- msd_to_d(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2)

esci <- psych::cohen.d.ci(d = d, n1 = n_right, n2 = n_left, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_right, n2 = n_left,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
```{r}
measure <- "Flexibility"
m1 <- input %>%
  filter(handedness == "right" & ttct_measure == measure) %>%
  .[["mean"]]
m2 <- input %>%
  filter(handedness == "left" & ttct_measure == measure) %>%
  .[["mean"]]
sd1 <- input %>%
  filter(handedness == "right" & ttct_measure == measure) %>%
  .[["sd"]]
sd2 <- input %>%
  filter(handedness == "left" & ttct_measure == measure) %>%
  .[["sd"]]

d <- msd_to_d(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2)

esci <- psych::cohen.d.ci(d = d, n1 = n_right, n2 = n_left, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_right, n2 = n_left,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
```{r}
measure <- "Originality"
m1 <- input %>%
  filter(handedness == "right" & ttct_measure == measure) %>%
  .[["mean"]]
m2 <- input %>%
  filter(handedness == "left" & ttct_measure == measure) %>%
  .[["mean"]]
sd1 <- input %>%
  filter(handedness == "right" & ttct_measure == measure) %>%
  .[["sd"]]
sd2 <- input %>%
  filter(handedness == "left" & ttct_measure == measure) %>%
  .[["sd"]]

d <- msd_to_d(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2)

esci <- psych::cohen.d.ci(d = d, n1 = n_right, n2 = n_left, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_right, n2 = n_left,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
```{r}
measure <- "Elaboration"
m1 <- input %>%
  filter(handedness == "right" & ttct_measure == measure) %>%
  .[["mean"]]
m2 <- input %>%
  filter(handedness == "left" & ttct_measure == measure) %>%
  .[["mean"]]
sd1 <- input %>%
  filter(handedness == "right" & ttct_measure == measure) %>%
  .[["sd"]]
sd2 <- input %>%
  filter(handedness == "left" & ttct_measure == measure) %>%
  .[["sd"]]

d <- msd_to_d(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2)

esci <- psych::cohen.d.ci(d = d, n1 = n_right, n2 = n_left, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_right, n2 = n_left,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
