<!-- Dependencies: tidyverse, psych, common/pretty_table.R -->

Shobe, E. R., Ross, N. M., & Fleck, J. I. (2009). Influence of handedness and bilateral eye movements on creativity. Brain and Cognition, 71(3), 204–214. https://doi.org/10.1016/j.bandc.2009.08.017

Task details: "An adaptation of the Alternate Uses Test (Chamorro-Premuzic, 2006) was used to measure creativity. This adaptation consisted of 20 common items (e.g. paper-clip, pencil, shoe, for full list see Appendix A). We used 15 items from the original Alternate Uses Test (Christensen et al., 1960) and five from a common word bank (Snodgrass & Vanderwart, 1980)"

AUT scoring: "Responses on the Alternate Uses Test were scored on five differ- ent sub-scores: (a) fluency, indicated by the total number of uses listed per item (regardless of ‘quality’ or appropriateness); (b) originality, indicated by the number of responses provided by 0–5% pf participants (3 points), 6–10% (2 points) or 11–15% (1 point) of all participants in the sample; (c) amount of detail or elaboration provided for each use (on a 0–5 point scale); (d) flexibility or the num- ber of ‘categorically’ distinct answers (1 point for each distinct ‘category’ of uses); and (e) appropriateness or usefulness of responses (1 point for each ‘appropriate’ response)."

Handedness measure: "Handedness was measured using a modification of the Edinburgh Handedness Inventory (Oldfield, 1971), an instrument shown to be reliable and well-validated (Bryden, 1977). Partici- pants were asked to indicate their preference (always, usually, no preference) of hand use for 10 activities from the Edinburgh Handedness Inventory (e.g., writing, drawing, throwing). Handedness scores for each participant ranged from 100 (perfectly right- handed) to 100 (perfectly left-handed)."

To make handedness groups, they took a median split on EHI (-100, +100; median 77.5), and excluded the one strong left hander (-100). This made two groups: 30 mixed handers, 32 right handers.

All participants were assigned randomly into one of two groups: control or eye movement. Because the eye movement condition may influence AUT performance, the control condition is most relevant for the present analysis. Unfortunately, the exact n by handedness group in the control condition isn't known (we know the totals for each condition (30 and 32), and for each handedness group (30 and 32), but not for each handedness group in each condition). Equal n's in each handedness group are impossible, and the only mathematical restriction is that there are the same number of strong righty controls and mixedy eye movers.

For this control condition, we have group means, F-values with df. Cohen's D can be calculated from the F values, if we assume that group n's are roughly equal. This assumption seems reasonable, and is made here for effect extraction. 

The exact n is known for the overall group comparison (collapsing across control and eye movement conditions). The direction of all effects is the same as in the control condition. For this less relevant (to meta-analysis) comparison, one could calculate an exact value for Cohen's D.


### {.tabset}

```{r}
study <- "shobe_2009"
task <- "AUT"
```

#### Within control condition (most relevant, but n's unknown)
```{r}
## There were 30 participants total in the control condition
## In order to calculate an effect size, we will assume equal group sizes
n_total <- 30
n_strong <- 15
n_mixed <- 15
```

```{r}
handedness_measure <- "EHI"
rl_sm <- "S/M"
es_type <- "d"
```

```{r}
measure <- "Fluency"

f <- 4.2
m_mixed <- 3.05
m_strong <- 2.3

t <- f_to_t(f = f)
d <- t_to_d_totaln(t, n_total)

## Change sign to indicate mixedy advantage
d <- -d
esci <- psych::cohen.d.ci(d = d, n = n_total, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, approx Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

```{r}
measure <- "Elaboration"

f <- 5.4
m_mixed <- 2.54
m_strong <- 1.95

t <- f_to_t(f = f)
d <- t_to_d_totaln(t, n_total)

## Change sign to indicate mixedy advantage
d <- -d
esci <- psych::cohen.d.ci(d = d, n = n_total, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, approx Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

```{r}
measure <- "Originality"

f <- 9.14
m_mixed <- 3.06
m_strong <- 1.03

t <- f_to_t(f = f)
d <- t_to_d_totaln(t, n_total)

## Change sign to indicate mixedy advantage
d <- -d
esci <- psych::cohen.d.ci(d = d, n = n_total, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, approx Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

```{r}
measure <- "Flexibility" ## "Categorical distinctiveness"

f <- 9.46
m_mixed <- 2.4
m_strong <- 1.5

t <- f_to_t(f = f)
d <- t_to_d_totaln(t, n_total)

## Change sign to indicate mixedy advantage
d <- -d
esci <- psych::cohen.d.ci(d = d, n = n_total, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, approx Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

```{r}
measure <- "Appropriateness"

f <- 9.5
m_mixed <- 2.75
m_strong <- 1.75

t <- f_to_t(f = f)
d <- t_to_d_totaln(t, n_total)

## Change sign to indicate mixedy advantage
d <- -d
esci <- psych::cohen.d.ci(d = d, n = n_total, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, approx Ns",
          include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

#### Collapsing across conditions (less relevant, but n's known)
```{r}
n_strong <- 32
n_mixed <- 30
```

```{r}
measure <- "Fluency (both conditions)"

m_mixed <- 3.09
se_mixed <- 0.19
m_strong <- 2.44
se_strong <- 0.18

## SD = SEM * sqrt(n)
d <- msd_to_d(m1 = m_strong, sd1 = se_strong * sqrt(n_strong),
              m2 = m_mixed, sd2 = se_mixed * sqrt(n_mixed))

esci <- psych::cohen.d.ci(d = d, n1 = n_strong, n2 = n_mixed, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, Ns",
          include = 0
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

```{r}
measure <- "Flexibility (both conditions)" ## "Categorical distinctiveness"

m_mixed <- 2.45
se_mixed <- 0.142
m_strong <- 1.67
se_strong <- 0.13

## SD = SEM * sqrt(n)
d <- msd_to_d(m1 = m_strong, sd1 = se_strong * sqrt(n_strong),
              m2 = m_mixed, sd2 = se_mixed * sqrt(n_mixed))

esci <- psych::cohen.d.ci(d = d, n1 = n_strong, n2 = n_mixed, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, Ns",
          include = 0
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

```{r}
measure <- "Appropriateness (both conditions)"
m_mixed <- 2.70
se_mixed <- 0.16
m_strong <- 1.84
se_strong <- 0.15

## SD = SEM * sqrt(n)
d <- msd_to_d(m1 = m_strong, sd1 = se_strong * sqrt(n_strong),
              m2 = m_mixed, sd2 = se_mixed * sqrt(n_mixed))

esci <- psych::cohen.d.ci(d = d, n1 = n_strong, n2 = n_mixed, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, Ns",
          include = 0
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

```{r}
measure <- "Originality (both conditions)"
m_mixed <- 3.35
se_mixed <- 0.28
m_strong <- 1.84
se_strong <- 0.27

## SD = SEM * sqrt(n)
d <- msd_to_d(m1 = m_strong, sd1 = se_strong * sqrt(n_strong),
              m2 = m_mixed, sd2 = se_mixed * sqrt(n_mixed))

esci <- psych::cohen.d.ci(d = d, n1 = n_strong, n2 = n_mixed, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, Ns",
          include = 0
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```

```{r}
measure <- "Elaboration (both conditions)"
m_mixed <- 2.5
se_mixed <- 0.18
m_strong <- 2.1
se_strong <- 0.18

## SD = SEM * sqrt(n)
d <- msd_to_d(m1 = m_strong, sd1 = se_strong * sqrt(n_strong),
              m2 = m_mixed, sd2 = se_mixed * sqrt(n_mixed))

esci <- psych::cohen.d.ci(d = d, n1 = n_strong, n2 = n_mixed, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          n1 = n_strong, n2 = n_mixed,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From Ms, SDs, Ns",
          include = 0
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
