<!-- Dependencies: tidyverse, psych, common/pretty_table.R -->

Turner, C. E., Hahn, M. E., & Kellogg, R. T. (2017). Semantic processing in the left versus right cerebral hemispheres following unilateral hand contractions. Laterality: Asymmetries of Body, Brain and Cognition, 22(2), 219–232. https://doi.org/10.1080/1357650X.2016.1154861

The study reports this result for the correlation between EHI score and RAT score (number of problems answered correctly in 15 minutes)
"We also examined whether the laterality quotients of participants were
related to task performance. Scores of above 75–80 indicate strong right
handedness and in the vast majority of cases, LH dominance. The laterality
quotient was not reliably related to remote associate scores (r = .07)."

The formula for "r" was not reported. I will presume that it is a Pearson correlation coefficient, because this is standard when correlated continuous variables (EHI and RAT scores are both ordinal scores with many levels, which might be treated as continuous).
Because none were reported, I will assume that no covariates were included in this correlation analysis.

There were 60 participants total: 43 strong right, 17 non-right handers.


### {.tabset}
```{r}
study <- "turner_2017"
task <- "RAT"
```

```{r}
handedness_measure <- "EHI"
rl_sm <- "R/L"
es_type <- "rho"
```

```{r}
measure <- "Total problems solved in 15 minutes"
n <- 60
rho <- 0.07

esci <- rho_ci(rho, n, alpha = 0.05) ## Defined in lib/utils.R

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, effect = esci$rho, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From rho, n", include = 1
          )

esci %>% pretty_table(title = str_c(study, ", ", task, ": ", measure))
```
