### Pool effect sizes from raw proportions, using glmer() {.tabset}

With glmer, any number of variables can be modeled as random effects.

The model type "random (all) includes study, estimate, handedness comparison, and population (Students/Faculty/Professionals) as random effects. This model is appropriate because effect estimates might vary along all of these dimensions.

```{r}
label_var = "from raw proportions, with all random effects, using glmer()"

## Use cached table, if it exists
pooled_filename <- str_c("pooled effects ", label_var, " ", rl_sm_label, ".csv")
pooled_filepath <- here(pool_dir, "data", "proc", pooled_filename)
if (file.exists(pooled_filepath)) {
  pool_table <- readr::read_csv(pooled_filepath)
} else {
  sub <- pool_input
  glm_sub <- glm_input

  prof_vars <- sub[["profession"]] %>% unique()
  model_type_vars <- c("random (all)")

  ## Initialize table to store results
  ## Requires {pool_dir}/lib/tables.R/init_pool_table()
  pool_table <- init_pool_table()

  for (model_type_var in model_type_vars) {
    for (prof_var in prof_vars) {
      glm_sub_prof <- glm_sub %>% filter(profession == prof_var)
      meta_sub_prof <- sub %>% filter(profession == prof_var)
      pool_row <- glmm_makerow(glm_sub_prof, meta_sub_prof, profession = prof_var,
                   es_type = "OR", model_type = model_type_var, label = "glmer")
      pool_table <- pool_table %>% add_row(pool_row)
    }
  }
  ## Save to file
  readr::write_csv(pool_table, pooled_filepath)
}

## Print summary table
pool_table %>% pool_table_gt(title = label_var, groupname_col = "profession")

# ## Add results to full table (This will hold individual stueis and effect estimates)
# pool_table_full <- pool_table_full %>% add_row(pool_table)
```

```{r}
# ## Print summary table
# pool_table_full %>% pool_table_gt(title = label_var, groupname_col = "profession")
```

```{r}
# ## Save to file
# pool_full_filename <- str_c("pooled_effects_", rl_sm_label, ".csv")
# readr::write_csv(pool_table_full, here(pool_dir, "data", "output", pool_full_filename))
```

### Final table {.active}
```{r}
##TODO: add re-expression of odds ratios as rate ratios
label_var = "Final table"
# pool_table_full <- readr::read_csv(here(pool_dir, "data", "output", pool_full_filename))
# pool_final <- pool_table_full %>% filter(model_type == "random (all)")
ee_final <- pool_input

forest_table <- bind_rows(ee_final, pool_table) %>% arrange(profession, N, effect) %>%
    mutate(pL_creative = str_c(n_left_creative, "/", n_creative, "\n(", round(PL_creative, 2), "%)"),
           pL_control = str_c(n_left_control, "/", n_control, "\n(", round(PL_control, 2), "%)")) %>%
    select(profession, N, N_stu, study, rl_sm, group1, group2, pL_creative, pL_control, lower, effect, upper, p, I2, comparison, model_type, label, es_type, se)

forest_table %>% pool_table_gt(title = label_var, groupname_col = "profession")

## Save to file
ft_filename <- str_c("forest_table_", rl_sm_label, ".csv")
readr::write_csv(forest_table, here(pool_dir, "data", "output", ft_filename))
```

### Blank (collapse)