Hering, R., Catarci, T., & Steiner, T. (1995). Handedness in musicians. Functional Neurology, 10(1), 23–26.
[[PDF](https://drive.google.com/file/d/13VjEUD_IzfOKGe1zjGz2-wexaxrfmuhi/view?usp=sharing)]

This study reports the handedness of 382 professional orchestra players. Handedness was measured by asking participants whether they were "right, left or mixed handed."

This study does not include a control group.

I will report the R/(M+L) frequency as "R/L" For odds ratios, I have preferred SR/SL, because it is a more direct measure of handedness direction, with less noise that could wash out differences. But, for a single frequency with no control group, the right vs. nonright percentage might be easier to interpret and compare with other studies.

I will report the (R+L)/M frequency as "S/M."

### Load data from input file
```{r}
## Load and display input data
study <- "hering_1995"
input <- load_input(str_c(study, ".csv"))
pretty_table(input, title = str_c(study, ".csv"))
```

### Calculate effect sizes
```{r, results = "markup"}
es_study <- calculate_es(input, study, OR = F, RR = F, freq = T)
```
```{r}
## Display study results
es_study %>% display_study_es()

## Add study results to full results table
es <- es %>% add_row(es_study)
```
