---
title: "Tasks: Reproduce Zickert et al. (2018)"
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: kable
    highlight: zenburn
    editor_options:
      chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")
```

```{r lib, include = F}
## Test that this file exists in the expected place
## relative to project root
library(here)
here::i_am("analyses/professions/0_replicate_zickert/reproduce_zickert.Rmd",
           uuid = "3c5078d6-4469-4fd9-8b7a-2f95c6b9b319")


## Declare base directory for project component
script_dir <- here("analyses", "professions", "0_replicate_zickert")
fig_dir <- here(script_dir, "figures")

## Load Packages
library(here)
library(tidyverse)
library(RColorBrewer) ## For categorical color palette
library(knitr)
library(santoku) ## for approx equal n quantiles
library(emmeans)

#
## Source common (project-level) functions
source(here("analyses", "lib", "util.R")) # format_p(), numformat()
source(here("analyses", "lib", "tables.R")) # pretty_table()
source(here("analyses", "lib", "ci_functions.R"))
source(here("analyses", "lib", "es_functions.R"))
source(here("analyses", "lib", "gg_style.R"))
#
## Colors for plots
plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")
plot_color = plot_blue


use_cached_figs <- F
```

```{r load}
## Load the data
raw_data <- read_csv(here(script_dir, "data", "analysis_data.csv"),
                     col_types = cols(
  ID = col_character(),
  EHIscore = col_double(),
  EHIscore_2 = col_double(),
  age = col_character(),
  age_2 = col_double(),
  sex = col_character(),
  children_YN = col_character(),
  compl_children = col_double(),
  child_0total = col_double(),
  S_hand_pref = col_double(),
  S_art_crea = col_double(),
  S_prob_crea = col_double(),
  S_aggression = col_double(),
  S_health = col_double(),
  Cre_A_total = col_double(),
  A_10jaar_fight = col_character(),
  A_10jaar_fight_wins = col_character(),
  A_child_fight = col_character(),
  A_10jaar_scheld = col_character(),
  check_aggr2 = col_double(),
  H_2sick = col_character(),
  H_2sickdays = col_character(),
  H_comp = col_double(),
  H_allergy_YN = col_character(),
  H_allergens = col_character(),
  H_premat_YN = col_character(),
  H_dyslex_YN = col_character(),
  DT_fluency = col_double(),
  DT_originality = col_double(),
  DT_combined = col_double(),
  CT_cor2_per_unknown_math = col_double(),
  CT_cor2_per_unknown_verb = col_character(),
  CT_cor2_per_unknown_total = col_double(),
  EHI_HVK_5 = col_character(),
  select_slider_and_quest = col_double(),
  exclude_age_sex_weird = col_character(),
  ehi_miss = col_character(),
  H_sick = col_character(),
  H_sickdays = col_character(),
  H_3sick = col_double(),
  FAC1_2 = col_character(),
  FAC1_1 = col_double(),
  FAC1_6 = col_double(),
  FAC2_6 = col_double(),
  FAC3_6 = col_double(),
  FAC1_3 = col_double(),
  FAC1_4 = col_double(),
  FAC1_10 = col_double(),
  FAC2_10 = col_double(),
  FAC3_10 = col_double(),
  RES_23 = col_double(),
  RES_24 = col_double(),
  RES_25 = col_double(),
  RES_26 = col_double(),
  RES_27 = col_double(),
  Residual_1 = col_double(),
  Residual_2 = col_character(),
  Residual_3 = col_double(),
  Residual_4 = col_character(),
  allergy_DevianceResidual_1 = col_character(),
  DevianceResidual_1 = col_double(),
  DR_allerg = col_double(),
  DR_dyslex = col_double(),
  DevianceResidual_2 = col_double(),
  Residual_8 = col_double(),
  Resid_children_invert = col_double(),
  Residual_9 = col_character(),
  RES_28 = col_double(),
  `filter_$` = col_character(),
  RES_1 = col_character(),
  RES_2 = col_character(),
  RES_3 = col_double(),
  RES_4 = col_double(),
  RES_5 = col_double(),
  RES_6 = col_double(),
  RES_7 = col_double(),
  RES_8 = col_double(),
  Inverse_resid_fights_won = col_double(),
  Residual = col_double(),
  Residual_5 = col_double(),
  RES_9 = col_double(),
  Residual_6 = col_double(),
  Inverse_resid_dyslexia = col_double(),
  Inverse_resid_allergies = col_character()
))
```

```{r clean}
#### Clean the data

## Authors' exclusions:

# - had missing data on any of the questions that were used in the statistical analysis and were not optional (except for the number of children as this question was added to the questionnaire in a later stage of the project).
# - did not specify their sex as male or female.
# - were under the age of 15 years and over 100 years.
# - indicated that they have a temporary or permanent limitation in one oftheirarmsorhands.
# - gave nonsensical answers (e.g. being 20 years old having three grandchildren).

## Remove rows that readr could not parse
problem_rows <- problems(raw_data) |> pull(row)
base_data <- raw_data |>
  slice(-problem_rows) |>
## Apply authors' exclusions
  filter(
  `filter_$` =="Selected"
)


## Create an asymmetry score based on raw EHI values
base_data <- base_data |>
  mutate(EHI_abs = abs(EHIscore))

## Create categorical handedness variables
base_data <- base_data |> mutate(
  ## 0-split
  handedness_rl = case_when(EHIscore > 0 ~ "right",
                            EHIscore <= 0 ~ "left"),
  ## Abs. Extremes vs. betweens
  handedness_sm = case_when(
    EHIscore %in% c(-20, 20) ~ "strong",
    EHIscore < 20 & EHIscore > -20 ~ "mixed"
  ),
  ## Directional Extremes vs. betweens
    handedness_rml = factor(
    case_when(
      handedness_rl == "right" &
        handedness_sm == "strong" ~ "strong right",
      handedness_rl == "right" &
        handedness_sm == "mixed" ~ "mixed",
      handedness_rl == "left" &
        handedness_sm == "mixed" ~ "mixed",
      handedness_rl == "left" &
        handedness_sm == "strong" ~ "strong left"
    ),
    levels = c("strong left", "mixed", "strong right")
  ),
  ## Directional extremes vs. betweens, cut at 0
  handedness_rmml = factor(
    case_when(
      handedness_rl == "right" &
        handedness_sm == "strong" ~ "strong right",
      handedness_rl == "right" &
        handedness_sm == "mixed" ~ "mixed right",
      handedness_rl == "left" &
        handedness_sm == "mixed" ~ "mixed left",
      handedness_rl == "left" &
        handedness_sm == "strong" ~ "strong left"
    ),
    levels = c("strong left", "mixed left", "mixed right", "strong right")
  ),
  ## Three bins of equal number
  handedness_3q = santoku::chop_equally(
    EHIscore, groups = 3, labels = c("Left", "Mixed", "Right")),
  ## Median split (R/L)
  handedness_rl_median = case_when(
    EHIscore > median(EHIscore) ~ "right",
    EHIscore <= median(EHIscore) ~ "left"),
  ## Median split (S/M)
  handedness_sm_median = case_when(
    EHI_abs >= median(EHI_abs) ~ "strong",
    EHI_abs < median(EHI_abs) ~ "mixed"),
  ## Reproduce bins from Zickert et al. (2018)
  handedness_zickert = factor(
    case_when(
    (EHIscore >= -20 & EHIscore <= -16) ~ "SL",
    (EHIscore >= -15 & EHIscore <= -5) ~ "ML",
    (EHIscore >= -4 & EHIscore <= 4) ~ "NP",
    (EHIscore >= 5 & EHIscore <= 15) ~ "MR",
    (EHIscore >= 16 & EHIscore <= 20) ~ "SR",
  ),
    levels = c("SL", "ML", "NP", "MR", "SR")
  )
)

## filter to participants with fluency or originality data
## (All participants who have either have the other)
proc <- base_data |> filter(!is.na(DT_fluency))
## EHIscore are raw EHI scores.
## EHIscore_2 are squared EHI scores (which the authors used as their measure of laterality)
```

# {.tabset}

## Visualize effect of handedness on DT {.tabset}

```{r lib_plot_ehi_cor}
plot_ehi_cor <- function(data, x_var, y_var, title_var) {
  summary_data <- data |>
    group_by({{x_var}}) |>
    summarize(mean_dv = mean({{y_var}}),
              n = n())

  ## Do a loess plot
  g <- proc |> ggplot(aes(x = {{x_var}}, y = {{y_var}})) +
    geom_smooth(
      color = "gray80",
      fill = "gray80",
      method = "loess",
      alpha = .3,
      linewidth = 0
    ) +
    stat_summary(
      fun.data = mean_se,
      geom = "linerange",
      linetype = 1,
      color = "gray70",
      show.legend = F,
      linewidth = .5
    ) +
    geom_point(
      data = summary_data,
      aes(y = mean_dv, size = n),
      fill = plot_color,
      color = "gray20",
      shape = 21,
      show.legend = F
    ) +
    scale_size_area() +
    labs(title = title_var) +
    theme(aspect.ratio = 1 / 1) |>
    gg_style()

  return(g)
}

```


### Fluency

```{r}
#### All EHI values, -20 to +20 (41 bins)
fig_path_var <- here(fig_dir, "EHIscore_cor_41bins_Fluency.png")
if (use_cached_figs == F) {
  g <- plot_ehi_cor(proc, EHIscore, DT_fluency, "EHI (all 41 values)")
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}
include_graphics(fig_path_var)
```

```{r}
## 5 groups (Following Zickert)
fig_path_var <- here(fig_dir, "EHIscore_cor_zickbins_Fluency.png")
if (use_cached_figs == F) {
  g <- plot_ehi_cor(proc, handedness_zickert, DT_fluency,
                    title = "EHI: SL (-20:-16), MR (-15:-5), NP (-4:4), MR (5:15), SR (16:20)")
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}
include_graphics(fig_path_var)
```

### Originality

```{r}
#### All EHI values, -20 to +20 (41 bins)
fig_path_var <- here(fig_dir, "EHIscore_cor_41bins_Originality.png")
if (use_cached_figs == F) {
  g <- plot_ehi_cor(proc, EHIscore, DT_originality, "EHI (all 41 values)")
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}
include_graphics(fig_path_var)
```

```{r}
## 5 groups (Following Zickert)
fig_path_var <- here(fig_dir, "EHIscore_cor_zickbins_Originality.png")
if (use_cached_figs == F) {
  g <- plot_ehi_cor(proc, handedness_zickert, DT_originality,
                    title = "EHI: SL (-20:-16), MR (-15:-5), NP (-4:4), MR (5:15), SR (16:20)")
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}
include_graphics(fig_path_var)
```

### Originality/Fluency

```{r}
#### All EHI values, -20 to +20 (41 bins)
fig_path_var <- here(fig_dir, "EHIscore_cor_41bins_Combined.png")
if (use_cached_figs == F) {
  g <- plot_ehi_cor(proc, EHIscore, DT_combined, "EHI (all 41 values)")
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}
include_graphics(fig_path_var)
```

```{r}
## 5 groups (Following Zickert)
fig_path_var <- here(fig_dir, "EHIscore_cor_zickbins_Combined.png")
if (use_cached_figs == F) {
  g <- plot_ehi_cor(proc, handedness_zickert, DT_combined,
                    title = "EHI: SL (-20:-16), MR (-15:-5), NP (-4:4), MR (5:15), SR (16:20)")
  ggsave(fig_path_var, g, "png", height = 4, width = 8)
}
include_graphics(fig_path_var)
```

## Calculate Effect sizes {.tabset .tabset-pills .active}

```{r}
## Initialize results table
es <- tibble(
             study = character(),
             task = character(),
             measure = character(),
             h = character(),
             rl_sm = character(),
             n = integer(),
             n1 = integer(),
             n2 = integer(),
             es_type = factor(),
             lower = numeric(),
             effect = numeric(),
             upper = numeric(),
             notes = character(),
             include = logical()
             )
```


### R/L {.tabset}

#### Fluency (rho)
```{r}
study <- "zickert_2018"
task <- "AUT"
handedness_measure <- "EHI"
rl_sm <- "R/L"
es_type <- "rho"
measure <- "Fluency"


cor_results <- cor.test(proc$EHIscore, proc$DT_fluency)

df <- cor_results$parameter[["df"]]
n <- cor_results$parameter[["df"]] + 2
rho <- cor_results$estimate

n_left <- proc |> filter(handedness_rl == "left") |> count() |> pull(n)
n_right <- proc |> filter(handedness_rl == "right") |> count() |> pull(n)

esci <- rho_ci(rho, n, alpha = 0.05)

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, n1 = n_right, n2 = n_left,
          effect = esci$rho, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From raw data", include = 1
          )

es |> tail(1) |> pretty_table()
```

#### Fluency (D)
```{r}
study <- "zickert_2018"
task <- "AUT"
handedness_measure <- "EHI"
rl_sm <- "R/L"
es_type <- "d"
measure <- "Fluency"

group_stats <- proc |>
  mutate(handedness = handedness_rl) |>
  group_by(handedness) |>
  summarize(
    n = n(),
    mean = mean(DT_fluency),
    sd = sd(DT_fluency)
  )

n1 <- group_stats |> filter(handedness == "right") |> pull(n)
n2 <- group_stats |> filter(handedness == "left") |> pull(n)
m1 <- group_stats |> filter(handedness == "right") |> pull(mean)
m2 <- group_stats |> filter(handedness == "left") |> pull(mean)
sd1 <- group_stats |> filter(handedness == "right") |> pull(sd)
sd2 <- group_stats |> filter(handedness == "left") |> pull(sd)

d <- msd_to_d(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2)

esci <- psych::cohen.d.ci(d = d, n1 = n1, n2 = n2, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          h = handedness_measure, rl_sm = "R/L",
          n = n1 + n2, n1 = n1, n2 = n2,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          notes = "From raw data", include = 1
          )

es |> tail(1) |> pretty_table()
```


#### Originality (rho)

```{r}
study <- "zickert_2018"
task <- "AUT"
handedness_measure <- "EHI"
rl_sm <- "R/L"
es_type <- "rho"
measure <- "Originality"


cor_results <- cor.test(proc$EHIscore, proc$DT_originality)

df <- cor_results$parameter[["df"]]
n <- cor_results$parameter[["df"]] + 2
rho <- cor_results$estimate

n_left <- proc |> filter(handedness_rl == "left") |> count() |> pull(n)
n_right <- proc |> filter(handedness_rl == "right") |> count() |> pull(n)

esci <- rho_ci(rho, n, alpha = 0.05)

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, n1 = n_right, n2 = n_left,
          effect = esci$rho, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From raw data", include = 1
          )

es |> tail(1) |> pretty_table()
```


#### Originality (D)

```{r}
study <- "zickert_2018"
task <- "AUT"
handedness_measure <- "EHI"
rl_sm <- "R/L"
es_type <- "d"
measure <- "Originality"

group_stats <- proc |>
  mutate(handedness = handedness_rl) |>
  group_by(handedness) |>
  summarize(
    n = n(),
    mean = mean(DT_originality),
    sd = sd(DT_originality)
  )

n1 <- group_stats |> filter(handedness == "right") |> pull(n)
n2 <- group_stats |> filter(handedness == "left") |> pull(n)
m1 <- group_stats |> filter(handedness == "right") |> pull(mean)
m2 <- group_stats |> filter(handedness == "left") |> pull(mean)
sd1 <- group_stats |> filter(handedness == "right") |> pull(sd)
sd2 <- group_stats |> filter(handedness == "left") |> pull(sd)

d <- msd_to_d(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2)

esci <- psych::cohen.d.ci(d = d, n1 = n1, n2 = n2, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          h = handedness_measure, rl_sm = "R/L",
          n = n1 + n2, n1 = n1, n2 = n2,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          notes = "From raw data", include = 1
          )

es |> tail(1) |> pretty_table()
```


### S/M {.tabset}

#### Fluency (rho)

```{r}
study <- "zickert_2018"
task <- "AUT"
handedness_measure <- "EHI"
rl_sm <- "S/M"
es_type <- "rho"
measure <- "Fluency"


cor_results <- cor.test(proc$EHI_abs,
                        proc$DT_fluency)

df <- cor_results$parameter[["df"]]
n <- cor_results$parameter[["df"]] + 2
rho <- cor_results$estimate

n_left <- proc |> filter(handedness_sm == "mixed") |> count() |> pull(n)
n_right <- proc |> filter(handedness_sm == "strong") |> count() |> pull(n)

esci <- rho_ci(rho, n, alpha = 0.05)

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, n1 = n_right, n2 = n_left,
          effect = esci$rho, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From raw data (unbalanced groups)", include = 1
          )

es |> tail(1) |> pretty_table()

```
<br>
<br>

#### Fluency (D)

"Strong": EHI extremes of +-20; "Mixed": everyone in-between (Unbalanced groups: there are more lefties than righties).
```{r}
study <- "zickert_2018"
task <- "AUT"
handedness_measure <- "EHI"
rl_sm <- "S/M"
es_type <- "d"
measure <- "Fluency"

group_stats <- proc |>
  mutate(handedness = handedness_sm) |>
  group_by(handedness) |>
  summarize(
    n = n(),
    mean = mean(DT_fluency),
    sd = sd(DT_fluency)
  )

n1 <- group_stats |> filter(handedness == "strong") |> pull(n)
n2 <- group_stats |> filter(handedness == "mixed") |> pull(n)
m1 <- group_stats |> filter(handedness == "strong") |> pull(mean)
m2 <- group_stats |> filter(handedness == "mixed") |> pull(mean)
sd1 <- group_stats |> filter(handedness == "strong") |> pull(sd)
sd2 <- group_stats |> filter(handedness == "mixed") |> pull(sd)

d <- msd_to_d(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2)

esci <- psych::cohen.d.ci(d = d, n1 = n1, n2 = n2, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          h = handedness_measure, rl_sm = rl_sm,
          n = n1 + n2, n1 = n1, n2 = n2,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          notes = "From raw data (unbalanced groups)", include = 1
          )

es |> tail(1) |> pretty_table()
```
<br>

#### Originality (rho)

```{r}
study <- "zickert_2018"
task <- "AUT"
handedness_measure <- "EHI"
rl_sm <- "S/M"
es_type <- "rho"
measure <- "Originality"


cor_results <- cor.test(proc$EHI_abs,
                        proc$DT_originality)

df <- cor_results$parameter[["df"]]
n <- cor_results$parameter[["df"]] + 2
rho <- cor_results$estimate

n_left <- proc |> filter(handedness_sm == "mixed") |> count() |> pull(n)
n_right <- proc |> filter(handedness_sm == "strong") |> count() |> pull(n)

esci <- rho_ci(rho, n, alpha = 0.05)

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          n = n, n1 = n_right, n2 = n_left,
          effect = esci$rho, lower = esci$lower, upper = esci$upper,
          h = handedness_measure, rl_sm = rl_sm,
          notes = "From raw data (unbalanced groups)", include = 1
          )

es |> tail(1) |> pretty_table()

```

#### Originality (D)

"Strong": EHI extremes of +-20; "Mixed": everyone in-between (Unbalanced groups: there are more lefties than righties).
```{r}
study <- "zickert_2018"
task <- "AUT"
handedness_measure <- "EHI"
rl_sm <- "S/M"
es_type <- "d"
measure <- "Originality"

group_stats <- proc |>
  mutate(handedness = handedness_sm) |>
  group_by(handedness) |>
  summarize(
    n = n(),
    mean = mean(DT_originality),
    sd = sd(DT_originality)
  )

n1 <- group_stats |> filter(handedness == "strong") |> pull(n)
n2 <- group_stats |> filter(handedness == "mixed") |> pull(n)
m1 <- group_stats |> filter(handedness == "strong") |> pull(mean)
m2 <- group_stats |> filter(handedness == "mixed") |> pull(mean)
sd1 <- group_stats |> filter(handedness == "strong") |> pull(sd)
sd2 <- group_stats |> filter(handedness == "mixed") |> pull(sd)

d <- msd_to_d(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2)

esci <- psych::cohen.d.ci(d = d, n1 = n1, n2 = n2, alpha = .05) %>%
  as_tibble()

es <- es %>%
  add_row(study = study, task = task, measure = measure, es_type = es_type,
          h = handedness_measure, rl_sm = rl_sm,
          n = n1 + n2, n1 = n1, n2 = n2,
          lower = esci$lower, effect = esci$effect, upper = esci$upper,
          notes = "From raw data (unbalanced groups)", include = 1
          )

es |> tail(1) |> pretty_table()
```
<br>

### Pairwise differences {.tabset}

#### Fluency

Test for pairwise differences between handedness groups.
```{r}
lm1 <- lm(data = proc, formula = DT_fluency ~ handedness_rml)
emmeans(lm1, ~handedness_rml) |>
  contrast("pairwise", infer = T) |>
  as_tibble() |>
  format_p.value() |>
  pretty_table("Pairwise differences in fluency by handedness group (3 bins)")
```
<br>
```{r}
emmeans(lm1, ~handedness_rml) |>
  summary(infer = T) |>
  format_p.value() |>
  pretty_table("Estimated fluency for each handedness group (3 bins)")
```

<br>
```{r}
lm1 <- lm(data = proc, formula = DT_fluency ~ handedness_rmml)
emmeans(lm1, ~handedness_rmml) |>
  contrast("pairwise", infer = T) |>
  as_tibble() |>
  format_p.value() |>
  pretty_table("Pairwise differences in Fluency by handedness group (4 bins)")
```
<br>
```{r}
emmeans(lm1, ~handedness_rmml) |>
  summary(infer = T) |>
  format_p.value() |>
  pretty_table("Estimated Fluency for each handedness group (4 bins)")
```
<br>
```{r}
proc |> group_by(handedness_rmml) |>
  summarize(n = n(),
            mean = mean(DT_fluency),
            sd = sd(DT_fluency),
            sem = sd/(sqrt(n))
  ) |>
  pretty_table("Group counts and raw means (Fluency)")
```


#### Originality
Test for pairwise differences between handedness groups.
```{r}
lm1 <- lm(data = proc, formula = DT_originality ~ handedness_rml)
emmeans(lm1, ~handedness_rml) |>
  contrast("pairwise", infer = T) |>
  as_tibble() |>
  format_p.value() |>
  pretty_table("Pairwise differences in Originality by handedness group (3 bins)")
```
<br>
```{r}
emmeans(lm1, ~handedness_rml) |>
  summary(infer = T) |>
  format_p.value() |>
  pretty_table("Estimated Originality for each handedness group (3 bins)")
```

<br>
```{r}
lm1 <- lm(data = proc, formula = DT_originality ~ handedness_rmml)
emmeans(lm1, ~handedness_rmml) |>
  contrast("pairwise", infer = T) |>
  as_tibble() |>
  format_p.value() |>
  pretty_table("Pairwise differences in originality by handedness group (4 bins)")
```
<br>
```{r}
emmeans(lm1, ~handedness_rmml) |>
  summary(infer = T) |>
  format_p.value() |>
  pretty_table("Estimated originality for each handedness group (4 bins)")
```
<br>
```{r}
proc |> group_by(handedness_rmml) |>
  summarize(n = n(),
            mean = mean(DT_originality),
            sd = sd(DT_originality),
            sem = sd/(sqrt(n))
  ) |>
  pretty_table("Group counts and raw means (Originality)")
```

### Summary {.active}
```{r}
pal <- brewer.pal(9, "Pastel1")

es <- es %>%
  mutate(es_type_labels = case_when(
            es_type == "d" ~ "Group differences: Cohen's D",
            es_type == "d_p" ~ "Group differences: Cohen's D (partial)",
            es_type == "rho" ~ "Correlations: Pearson's ρ",
            es_type == "rho_p" ~ "Correlations: Pearson's ρ (partial)",
            es_type == "beta" ~ "Correlations: Regression Coeffient β"
            )
        )

es %>%
  filter(task == "AUT") %>%
  select(es_type_labels, study, task, measure, h, rl_sm, n, n1, n2, lower, effect, upper, notes) %>%
  arrange(task, study, measure, effect) %>%
  pretty_table(title = "AUT", groupname_col = "es_type_labels") |>
  data_color(columns = study,
  colors = scales::col_factor(palette = pal,
     domain = NULL)
          ) |>
  data_color(
    columns = c(lower, effect, upper),
    colors = scales::col_bin(
        bins = 3,
        na.color = "#f7f7f7",
      palette = c(
        "#f1b6da", "#f7f7f7", "#b8e186"),
      domain = c(-2.7, 2.7))
  )
```
