---
title: "Tasks: extract effect sizes (Creativity and Handedness)"
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: kable
    highlight: zenburn
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")
options(knitr.duplicate.label = "allow")
```

```{r lib, include = F}
## Test that this file exists in the expected place
## relative to project root
here::i_am("analyses/tasks/1_extract/extract.Rmd",
           uuid = "11fea017-684e-4405-a555-bdc7e38b6e0b")

## Load Packages
library(here)
library(tidyverse)
library(gt) ## To print tables
library(RColorBrewer) ## For categorical color palette
requireNamespace("psych") ## To find CI for Cohen's D
requireNamespace("MBESS") ## To find CI for partial eta^2

## Source common (project-level) functions
source(here("analyses", "lib", "util.R")) # format_p(), numformat()
source(here("analyses", "lib", "tables.R")) # pretty_table()
source(here("analyses", "lib", "conversions.R")) # pretty_table()
source(here("analyses", "lib", "es_functions.R"))
source(here("analyses", "lib", "util.R"))
source(here("analyses", "lib", "agg_functions.R"))

## Declare base directory for this project component
extract_dir <- here("analyses", "tasks", "1_extract")

## For development (when knitting, these will be sourced as children
## In the section "Functions for finding effect sizes...")
## These source() calls must be commented out when knitting
source(knitr::purl(here(extract_dir, "lib", "es_functions.Rmd"), quiet = TRUE))
source(here("analyses", "lib", "ci_functions.R"))
```

<!-- ## Blank (collapse) {.active} -->

# Effect size calculations {.tabset}

```{r init_results_tbl, include = F}
## Initialize results table
es <- tibble(
             study = character(),
             task = character(),
             measure = character(),
             h = character(),
             rl_sm = character(),
             n = integer(),
             n1 = integer(),
             n2 = integer(),
             es_type = factor(),
             lower = numeric(),
             effect = numeric(),
             upper = numeric(),
             notes = character(),
             include = logical()
             )
```

Note on coding effect directions: in all analyses, right/strong handers are coded as "1", mixed/left handers are coded as "0" (and, right/strong handers are coded as "n1"/"m1"..., mixed/left handers are "n2"/m2"...).


## Bosch 2013 (TTCT-F)
```{r child = here(extract_dir, "components", "bosch_2013_ttct-f.Rmd")}
```

## Burke et al. 1989 (TTCT-F)
```{r child = here(extract_dir, "components", "burke_1989_ttct-f.Rmd")}
```

## Burke et al. 1989 (TTCT-V)
```{r child = here(extract_dir, "components", "burke_1989_ttct-v.Rmd")}
```

## Coren 1995 (AUT)
```{r child = here(extract_dir, "components", "coren_1995_aut.Rmd")}
```

## Falleta 1986 (TTCT-F)
```{r child = here(extract_dir, "components", "falleta_1986_ttct-f.Rmd")}
```

## Bosch 2013 (TTCT-V)
```{r child = here(extract_dir, "components", "bosch_2013_ttct-v.Rmd")}
```

## Everatt 1999 (AUT)
```{r child = here(extract_dir, "components", "everatt_1999_aut.Rmd")}
```

## Everatt 1999 (TTCT-F)
```{r child = here(extract_dir, "components", "everatt_1999_ttct-f.Rmd")}
```

## Feen et al. 2020 (AUT)
```{r child = here(extract_dir, "components", "feen_2020_aut.Rmd")}
```

## Felton 2017 (RAT)
```{r child = here(extract_dir, "components", "felton_2017_rat.Rmd")}
```

## Felton 2017 (AUT)
```{r child = here(extract_dir, "components", "felton_2017_aut.Rmd")}
```

## Folley 2006 (AUT)
```{r child = here(extract_dir, "components", "folley_2006_aut.Rmd")}
```

## Hattie & Fitzgerald 1983 (RAT)
```{r child = here(extract_dir, "components", "hattie_1983_rat.Rmd")}
```

## Hattie & Fitzgerald 1983 (TTCT-F)
```{r child = here(extract_dir, "components", "hattie_1983_ttct-f.Rmd")}
```

## Hattie & Fitzgerald, 1983 (TTCT-V)
```{r child = here(extract_dir, "components", "hattie_1983_ttct-v.Rmd")}
```

## Jones et al. 2011 (AUT)
```{r child = here(extract_dir, "components", "jones_2011_aut.Rmd")}
```

## Jones et al. 2011 (RAT)
```{r child = here(extract_dir, "components", "jones_2011_rat.Rmd")}
```

## Katz 1980 (RAT)
```{r child = here(extract_dir, "components", "katz_1980_rat.Rmd")}
```

## Katz 1980 (TTCT-V)
```{r child = here(extract_dir, "components", "katz_1980_ttct-v.Rmd")}
```

## Katz 1980 (TTCT-F)
```{r child = here(extract_dir, "components", "katz_1980_ttct-f.Rmd")}
```

## Newland 1981 (TTCT-F)
```{r child = here(extract_dir, "components", "newland_1981_ttct-f.Rmd")}
```

## Turner 2016 (RAT)
```{r child = here(extract_dir, "components", "turner_2016_rat.Rmd")}
```

## Turner 2016 (AUT)
```{r child = here(extract_dir, "components", "turner_2016_aut.Rmd")}
```

## Turner 2017 (RAT)
```{r child = here(extract_dir, "components", "turner_2017_rat.Rmd")}
```

## Shobe et al. 2009 (AUT)
```{r child = here(extract_dir, "components", "shobe_2009_aut.Rmd")}
```

## Stewart & Clayson 1980 (TTCT-F)
```{r child = here(extract_dir, "components", "stewart_1980_ttct-f.Rmd")}
```

## Zickert et al. 2018 (AUT)
```{r child = here(extract_dir, "components", "zickert_2018_aut.Rmd")}
```

## Blank (collapse) {.active}

# Results {.tabset}

```{r, include = F}
pal <- brewer.pal(9, "Pastel1")
```


```{r, include = F}
## Make "study" a factor
es <- es %>% mutate(study = as.factor(study))

## Make a column with group name labels
es <- es %>%
  mutate(es_type_labels = case_when(
            es_type == "d" ~ "Group differences: Cohen's D",
            es_type == "rho" ~ "Correlations: Pearson's rho",
            es_type == "rho_p" ~ "Correlations: Pearson's rho (partial)",
            es_type == "beta" ~ "Correlations: Regression Coeffient β"
            )
        )

## Calculate total n for all studies
es <- es %>%
  mutate(n = case_when(
                       is.na(n) ~ (n1 + n2),
                       TRUE ~ n
                       )
  )

## Recode study names
es <- es |>
  mutate(study = study |>
      recode("jones_2011" = "Jones et al. (2011)",
             "coren_1995" = "Coren (1995)",
             "felton_2017" = "Felton (2017)",
             "folley_2006" = "Folley (2006)",
             "everatt_1999" = "Everatt et al. (1999)",
             "zickert_2018" = "Zickert et al. (2018)",
             "falleta_1986" = "Falleta (1986)",
             "bosch_2013" = "Bosch (2013)",
             "turner_2016" = "Turner (2016)",
             "turner_2017" = "Turner et al. (2017)",
             "katz_1980" = "Katz (1980)",
             "hattie_1983" = "Hattie & Fitzgerald (1983)",
             "shobe_2009" = "Shobe et al. (2009)",
             "feen_2020" = "Feen et al. (2020)",
             "newland_1981" = "Newland (1981)",
             "stewart_1980" = "Stewart & Clayson (1980)",
             "burke_1989" = "Burke et al. (1989)"
             )
  )

## Write final table to file
extracted_effects <- es %>%
  filter(include == 1) %>%
  select(study, task, measure, h, rl_sm, n, n1, n2,
         es_type, lower, effect, upper, notes)
write_csv(extracted_effects, here(extract_dir, "data", "output", "extracted_effects.csv"))
```

The columns "lower" and "upper" are 95% CI bounds around effect sizes. "h" is handedness measure, and "rl_sm" shows whether the effect reflects handedness direction ("R/L": right/left) or strength ("S/M": strong/mixed). Positive effect sizes indicate a right- or strong-hander advantage. "n1" represents right/strong handers, "n2", mixed/left handers.

Effect sizes and confidence intervals are rounded to the 3rd decimal, with trailing zeroes removed.

## Full table (All tasks) {.active}
```{r, echo = F}
# Make single table grouped by effect size type and study.

## Make a column with group name labels
es <- es %>%
  mutate(es_type_labels = case_when(
            es_type == "d" ~ "Group differences: Cohen's D",
            es_type == "d_p" ~ "Group differences: Cohen's D (partial)",
            es_type == "rho" ~ "Correlations: Pearson's ρ",
            es_type == "rho_p" ~ "Correlations: Pearson's ρ (partial)",
            es_type == "beta" ~ "Correlations: Regression Coeffient β"
            )
        )


## Display table with column labels
es %>%
  filter(include == 1) %>%
  select(es_type_labels, study, task, measure, h, rl_sm, n, n1, n2, lower, effect, upper, notes) %>%
  arrange(task, study, measure, effect) %>%
  pretty_table(title = "All divergent thinking tasks", groupname_col = "es_type_labels") %>%
  data_color(columns = study,
             colors = scales::col_factor(palette = pal,
                domain = NULL)
            ) %>%
  data_color(
    columns = c(lower, effect, upper),
    colors = scales::col_bin(
        bins = 3,
        na.color = "#f7f7f7",
      palette = c(
        "#f1b6da", "#f7f7f7", "#b8e186"),
      domain = c(-2.7, 2.7))
  )
```

## RAT

```{r, echo = F}
es %>%
  filter(include == 1 & task == "RAT") %>%
  select(es_type_labels, study, task, measure, h, rl_sm, n, n1, n2, lower, effect, upper, notes) %>%
  arrange(task, study, measure, effect) %>%
  pretty_table(title = "RAT", groupname_col = "es_type_labels") %>%
  data_color(columns = study,
             colors = scales::col_factor(palette = pal,
                domain = NULL)
            ) %>%
  data_color(
    columns = c(lower, effect, upper),
    colors = scales::col_bin(
        bins = 3,
        na.color = "#f7f7f7",
      palette = c(
        "#f1b6da", "#f7f7f7", "#b8e186"),
      domain = c(-2.7, 2.7))
  )
```

## AUT
```{r, echo = F}
es %>%
  filter(include == 1 & task == "AUT") %>%
  select(es_type_labels, study, task, measure, h, rl_sm, n, n1, n2, lower, effect, upper, notes) %>%
  arrange(task, study, measure, effect) %>%
  pretty_table(title = "AUT", groupname_col = "es_type_labels") %>%
  data_color(columns = study,
             colors = scales::col_factor(palette = pal,
                domain = NULL)
            ) %>%
  data_color(
    columns = c(lower, effect, upper),
    colors = scales::col_bin(
        bins = 3,
        na.color = "#f7f7f7",
      palette = c(
        "#f1b6da", "#f7f7f7", "#b8e186"),
      domain = c(-2.7, 2.7))
  )
```

## TTCT-F

```{r, echo = F}
es %>%
  filter(include == 1 & task == "TTCT(F)") %>%
  select(es_type_labels, study, task, measure, h, rl_sm, n, n1, n2, lower, effect, upper, notes) %>%
  arrange(task, study, measure, effect) %>%
  pretty_table(title = "TTCT-F", groupname_col = "es_type_labels") %>%
  data_color(columns = study,
             colors = scales::col_factor(palette = pal,
                domain = NULL)
            ) %>%
  data_color(
    columns = c(lower, effect, upper),
    colors = scales::col_bin(
        bins = 3,
        na.color = "#f7f7f7",
      palette = c(
        "#f1b6da", "#f7f7f7", "#b8e186"),
      domain = c(-2.7, 2.7))
  )
```

## TTCT-V

```{r, echo = F}
es %>%
  filter(include == 1 & task == "TTCT(V)") %>%
  select(es_type_labels, study, task, measure, h, rl_sm, n, n1, n2, lower, effect, upper, notes) %>%
  arrange(task, study, measure, effect) %>%
  pretty_table(title = "TTCT-V", groupname_col = "es_type_labels") %>%
  data_color(columns = study,
             colors = scales::col_factor(palette = pal,
                domain = NULL)
            ) %>%
  data_color(
    columns = c(lower, effect, upper),
    colors = scales::col_bin(
        bins = 3,
        na.color = "#f7f7f7",
      palette = c(
        "#f1b6da", "#f7f7f7", "#b8e186"),
      domain = c(-2.7, 2.7))
  )
```

