---
title: "Tasks: pool extracted effect sizes (Creativity and Handedness)"
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: kable
    highlight: zenburn
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

#rmarkdown::render(here("analyses", "tasks", "2_pool", "pool.Rmd"), "html_document")
```

```{r lib, include = F}
## Test that this file exists in the expected place
## relative to project root
here::i_am("analyses/tasks/2_pool/pool.Rmd",
           uuid = "f740a502-3803-4728-bf08-cf6b0b47c00d")

## Load Packages
library(here)
library(tidyverse)
library(gt) ## To print tables
library(RColorBrewer) ## For categorical color palette

## Source common (project-level) functions
source(here("analyses", "lib", "util.R")) # format_p(), numformat()
source(here("analyses", "lib", "tables.R")) # pretty_table()
source(here("analyses", "lib", "conversions.R")) # ci_to_se(), se_to_inv_var()
source(here("analyses", "lib", "ci_functions.R")) ## e.g., r2_to_rho

## Declare base directory for project component
extract_dir <- here("analyses", "tasks", "1_extract")
pool_dir <- here("analyses", "tasks", "2_pool")

## Source analysis-specific functions
source(here(pool_dir, "lib", "pool_functions.R"))
source(here(pool_dir, "lib", "util.R"))
source(here(pool_dir, "lib", "init_pool_table.R"))
```

```{r, include = F}
## Load extracted effect sizes
es_individual_full <- read_csv(here(extract_dir, "data", "output",
                        "extracted_effects.csv")) %>%
            select(-notes) %>%
          ## remove NAs (studies that report "null" with no stats)
            filter(!is.na(effect))
```
```{r, include = T}
## Calculate SE, "inverse variance" for each study
## (needed to directly calculate ES summaries)
es_individual_full <- es_individual_full %>%
  mutate(se = ci_to_se(n = n, lower = lower, upper = upper, alpha = 0.05),
         inv_var = se_to_inv_var(se)
         )
```

# Calculate pooled effect sizes {.tabset}

```{r, echo = F}
##TODO: Convert "r" values to standardized estimates, using
## Fisher's transform (Then re-calculate CI from z, n)

##TODO: Show forest plots
```

```{r}
## Recode RAT problems in es_individual_full
es_individual_full <- es_individual_full %>%
  mutate(measure = recode(measure,
                          "Total problems solved in 5 minutes" = "Problems solved",
                          "Total problems solved in 15 minutes" = "Problems solved",
                          "Problems solved out of 20, untimed" = "Problems solved",
                          "Problems solved out of 30 in 40 minutes" = "Problems solved",
                          "Problems solved out of 21" = "Problems solved"
                          )
)
```

## S/M + R/L {.tabset .tabset-pills}
Combining strong/mixed and left/right comparisons — strong/right advantage is coded as a positive effect.
```{r, echo = F}
## Initialize summary table
pool_table <- init_pool_table()

## Make sub-table
es_individual <- es_individual_full ## Do not filter by R/L, S/M
## Make table collapsing partial and simple effects
es_individual_collapse_partial <- es_individual %>%
  mutate(es_type = recode(es_type, rho_p = "rho", d_p = "d"))
```
```{r child = here(pool_dir, "components", "calculate_pooled_effects.Rmd")}
```
```{r}
## Save to file
pooled_filename <- "RAT-recode_pooled_effects_rlsm.csv"
readr::write_csv(pool_table, here(pool_dir, "data", "output", pooled_filename))
pooled_filename_rds <- "RAT-recode_pooled_effects_rlsm.rds"
saveRDS(pool_table, here(pool_dir, "data", "output", pooled_filename_rds))
```

## R/L {.tabset .tabset-pills}
Left/right comparisons only — right-hander advantage is coded as a positive effect.
```{r, echo = F}
pool_table <- init_pool_table()
es_individual <- es_individual_full %>% filter(rl_sm == "R/L")
es_individual_collapse_partial <- es_individual %>%
  mutate(es_type = recode(es_type, rho_p = "rho", d_p = "d"))
```
```{r child = here(pool_dir, "components", "calculate_pooled_effects.Rmd")}
```
```{r}
## Save to file
pooled_filename <- "RAT-recode_pooled_effects_rl.csv"
readr::write_csv(pool_table, here(pool_dir, "data", "output", pooled_filename))
pooled_filename_rds <- "RAT-recode_pooled_effects_rl.rds"
saveRDS(pool_table, here(pool_dir, "data", "output", pooled_filename_rds))
```

## S/M {.tabset .tabset-pills}
Strong/mixed comparisons only — strong-hander advantage is coded as a postive effect.
```{r, echo = F}
pool_table <- init_pool_table()
es_individual <- es_individual_full %>% filter(rl_sm == "S/M")
es_individual_collapse_partial <- es_individual %>%
  mutate(es_type = recode(es_type, rho_p = "rho", d_p = "d"))
```
```{r child = here(pool_dir, "components", "calculate_pooled_effects.Rmd")}
```
```{r}
## Save to file
pooled_filename <- "RAT-recode_pooled_effects_sm.csv"
readr::write_csv(pool_table, here(pool_dir, "data", "output", pooled_filename))
pooled_filename_rds <- "RAT-recode_pooled_effects_sm.rds"
saveRDS(pool_table, here(pool_dir, "data", "output", pooled_filename_rds))
```

<br>
<br>
