---
title: "Professions: Extract effect sizes (Creative Professions and Handedness) - Collapse Artist Occupations"
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: kable
    highlight: zenburn
    editor_options:
      chunk_output_type: console
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: 50px;
  margin-right: 50px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")
```

```{r lib, include = F}
## Test that this file exists in the expected place
## relative to project root
here::i_am("analyses/professions/1_extract/extract.Rmd",
           uuid = "41aed3d4-9a8b-438b-berd-811c655d9323")

## Load Packages
library(here)
library(tidyverse)
library(gt) ## To print tables
library(RColorBrewer) ## For categorical color palette
requireNamespace("epitools") ## To find OR/RR, CI
requireNamespace("PropCIs") ## To find score CI (Felix's rec)
requireNamespace("psych") # To find CI around cohen's D

## Source common (project-level) functions
source(here("analyses", "lib", "util.R")) # format_p(), numformat()
source(here("analyses", "lib", "tables.R")) # pretty_table()
source(here("analyses", "lib", "agg_functions.R"))

## Declare base directory for this project component
extract_dir <- here("analyses", "professions", "1_extract")

## Source analysis-specific functions
source(here(extract_dir, "lib", "init_es_table.R"))
source(here(extract_dir, "lib", "load_input.R"))
source(here(extract_dir, "lib", "calculate_es.R"))
source(here(extract_dir, "lib", "es_functions.R"))
```

# Procedure {.tabset}

Odds ratios were constructed based on frequency tables from each included studies. Confidence intervals for odds ratios were calculated with Agresti's score confidence interval formula, using the package PropCIs.

Agresti, A. (2013). An introduction to categorical data analysis (3rd ed). Wiley-Interscience.

# Effect size calculations {.tabset .tabset-pills}

An odds ratio greater than 1 indicates lefty/mixedy advantage.
"PL_\*" shows the percentage of lefties in creative and control groups.
"lower" and "upper" are 95% confidence intervals.
"group1" marks the creative group, "group2" the control group.

```{r, include = F}
## Initialize results table
es <- init_es_table()
```

## Peterson 1979 (Art/Architecture; Music) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "peterson_1979.Rmd")}
```

## Mebert & Michel 1980 (Art) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "mebert_1980.Rmd")}
```

## Coren & Porac 1982 (Art) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "coren_1982.Rmd")}
```

## Giotakos 2004 (Art/Music) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "giotakos_2004.Rmd")}
```

## Shettel-Neuber & O'Reilly 1983 (Art; Architecture) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "shettel-neuber_1983.Rmd")}
```

## Preti 2007 (Art; Music) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "preti_2007.Rmd")}
```


## Schacter & Ransil 1994 (Architecture) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "schacter_1996.Rmd")}
```

## Gotestam 1990 (Architecture; Music) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "gotestam_1990.Rmd")}
```

## Wood & Aggleton 1991 (Architecture) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "wood_1991.Rmd")}
```

## Aggleton et al. 1994 (Music) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "aggleton_1994.Rmd")}
```

## Quinan 1922 (Music) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "quinan_1922.Rmd")}
```

## Fry 1990 (Music) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "fry_1990.Rmd")}
```

## Oldfield 1969 (Music) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "oldfield_1969.Rmd")}
```

## Byrne 1974 (Music) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "byrne_1974.Rmd")}
```

## Cosenza & Mignoti 1993 (Music, Art, Architecture) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "cosenza_1993.Rmd")}
```

## Goodman 2014 / NLSY79, NLSY97 (Music, Art Architecture) {.tabset}
```{r child = here(extract_dir, "components", "es_calculations", "goodman_2014.Rmd")}
```

## Blank (collapse) {.active}

# Results {.tabset}
```{r child = here(extract_dir, "components", "results.Rmd")}
```

<br>
<br>
