---
title: "Professions: pool extracted effect sizes (Creativity and Handedness)"
author: ""
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: kable
    highlight: zenburn
    editor_options:
      chunk_output_type: console
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: 50px;
  margin-right: 50px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")
```

```{r lib, include = F}
## Test that this file exists in the expected place
## relative to project root
here::i_am("analyses/professions/2_pool/pool.Rmd",
           uuid = "3c5078d6-4869-4fd9-8b7a-2f95c6b9b316")

## Load Packages
library(here)
library(tidyverse)
library(gt) ## To print tables
library(RColorBrewer) ## For categorical color palette
library(lme4) # use glmer for odds ratio pooling
library(emmeans) # to find CI for glmm models
requireNamespace("meta")

## Source common (project-level) functions
source(here("analyses", "lib", "util.R")) # format_p(), numformat()
source(here("analyses", "lib", "tables.R")) # pretty_table()
source(here("analyses", "lib", "conversions.R")) # ci_to_se(), se_to_inv_var()

## Declare base directory for project component
extract_dir <- here("analyses", "professions", "1_extract")
pool_dir <- here("analyses", "professions", "2_pool")

## Source analysis-specific functions
source(here(pool_dir, "lib", "1_proc_ee.R"))
source(here(pool_dir, "lib", "2_make_glm_df.R"))
source(here(pool_dir, "lib", "pool_functions.R"))
source(here(pool_dir, "lib", "tables.R"))
```

```{r}
## MANUAL CACHING
## These files are manually cached:
## data/proc/glm_data.csv
## data/proc/pooled effects...
## To clear the cache, delete all files from data/proc/
```

```{r, echo = F}
## Load and process extracted effect size data
extracted_effects <- readr::read_csv(here(extract_dir, "data", "output",
                                          "extracted_effects.csv"))
## Requires: {pool_dir/lib/1_proc_ee.R
ee_proc <- proc_ee(extracted_effects)

## Create (or load cached) glm table, with one row for each observation)
## Requires: {pool_dir/lib/2_make_glm_df.R
glm_data <- make_glm_df(ee_proc)
```

<!-- # Procedure -->
<!-- ```{r child = here(pool_dir, "components", "procedure.Rmd")} -->
<!-- ``` -->

# Calculate pooled effect sizes for each profession {.tabset}

Pool estimates from studies with odds ratios for left or mixed handers between a creative and control group. Pool estimated odds ratios for each profession.

An odds ratio greater than 1 indicates lefty/mixedy advantage.

## R/L + S/M {.tabset .tabset-pills}
An odds ratio greater than one is a lefty/mixedy advantage.
```{r, echo = F}
rl_sm_label <- "rl_sm"
# pool_table_full <- init_pool_table()
pool_input <- ee_proc %>% filter(rl_sm == "R/L" | rl_sm == "S/M")
glm_input <- glm_data %>% filter(rl_sm == "R/L" | rl_sm == "S/M")
```
```{r child = here(pool_dir, "components", "calculate_pooled_effects.Rmd")}
```
```{r}
## Save pooled data to file
# pooled_filename <- str_c("pooled_effects_", rl_sm_label, ".csv")
# readr::write_csv(pool_table_full, here(pool_dir, "data", "output", pooled_filename))
#
```

## R/L {.tabset .tabset-pills .active}
Left/right comparisons only — an odds ratio greater than one is a lefty advantage.
```{r, echo = F}
rl_sm_var <- "R/L"
rl_sm_label <- "rl"
# pool_table_full <- init_pool_table()
pool_input <- ee_proc %>% filter(rl_sm == rl_sm_var)
glm_input <- glm_data %>% filter(rl_sm == rl_sm_var)
```
```{r child = here(pool_dir, "components", "calculate_pooled_effects.Rmd")}
```
```{r}
## Save pooled data to file <-
# pooled_filename <- str_c("pooled_effects_", rl_sm_label, ".csv")
# readr::write_csv(pool_table_full, here(pool_dir, "data", "output", pooled_filename))

# pooled_filename_rds <- str_c("pooled_effects_", rl_sm_label, ".rds")
# saveRDS(pool_table_full, here(pool_dir, "data", "output", pooled_filename_rds))
```

## S/M {.tabset .tabset-pills}
Strong/mixed comparisons only — an odds ratio greater than one is a mixedy advantage.
```{r, echo = F}
rl_sm_var <- "S/M"
rl_sm_label <- "sm"
# pool_table_full <- init_pool_table()
pool_input <- ee_proc %>% filter(rl_sm == rl_sm_var)
glm_input <- glm_data %>% filter(rl_sm == rl_sm_var)
```
```{r child = here(pool_dir, "components", "calculate_pooled_effects.Rmd")}
```
```{r}
## Save pooled data to file
# pool_full_filename <- str_c("pooled_effects_", rl_sm_label, ".csv")
# readr::write_csv(pool_table_full, here(pool_dir, "data", "output", pool_full_filename))

# pooled_filename_rds <- str_c("pooled_effects_", rl_sm_label, ".rds")
# saveRDS(pool_table_full, here(pool_dir, "data", "output", pooled_filename_rds))
```
<br>
<br>
