Here, I calculate fixed effects models "by hand" for task, measure, and effect size type, and display pooled estimates along with individual study estimates.

How to calculate summaries using fixed effects model
(Following https://perma.cc/96PS-FN7Z)

1. Find weights: inverse variance
    i) Find standard error of ES estimate (use 95% CI)
    i) Find variance (standard error squared)
    i) Find inverse variance (1/variance)
1. Estimate pooled effect size as the weighted average of each study's effect size
    i) Multiple each study's effect size with its weight.
    i) Sum these products across each effect
    i) Divide by the sum of all individual weights

The columns “lower” and “upper” are 95% CI bounds on the reported effect size (d or Pearson’s rho). “h” is handedness measure, and “rl_sm” shows whether the effect reflects handedness direction (“R/L”: right/left) or strength (“S/M”: strong/mixed). Positive effect sizes indicate a right- or strong-hander advantage. The table section headers show "measure - effect size type."

Confidence intervals are likely **overly wide**: they are calculated as the weighted average of individual confidence bound.
```{r, include = F, cache = T}
#### Calculate pooled ES for specified subgroups

## Define groups to calculate ES over
groups <- c("task", "measure", "es_type")

## Specify color palette for tables
pal <- brewer.pal(9, "Pastel1")

## TODO: Consider using Knapp-Hartung adjustments (Knapp & Hartung, 2003)
## to calculate the confidence interval around the pooled effect.
## https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/pooling-es.html

##TODO: Check results against metagen
## https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/pooling-es.html#pre-calculated-es

## Define function to make table showing pooled ES for each measure, ES type
make_measure_es_table <- function(es_combo, grouping_vars = c("measure", "es_type")) {
  es_combo %>%
    select(study, measure, h, rl_sm, es_type, N, n, n1, n2, inv_var,
           lower, effect, upper) %>%
    pretty_table(title = "RAT", groupname_col = grouping_vars) %>%
    # tbl_summary(by = es_type) %>%
    data_color(columns = study,
               colors = scales::col_factor(palette = pal,
                  domain = NULL)
              )
}
```

#### RAT
```{r, echo = F, cache = T}
es_task <- es_individual %>% filter(task == "RAT")
es_pooled <- pool_es_fixed(es_task, groups, "fixed")
es_combo <- combined_es(es_pooled, es_task, groups)
make_measure_es_table(es_combo)
```

##### Combine measures of total score
```{r, echo = F, cache = T}
groups <- c("task", "measure", "es_type")
measure_var <- "Problems solved"
es_task <- es_individual %>%
  filter(task == "RAT") %>%
  mutate(measure_orig = measure,
         measure_temp = case_when(
           measure == "Total problems solved in 5 minutes" ~ "Problems solved",
           measure == "Total problems solved in 15 minutes" ~ "Problems solved",
           measure == "Problems solved out of 20, untimed" ~ "Problems solved",
           measure == "Problems solved out of 30 in 40 minutes" ~ "Problems solved",
           measure == "Problems solved out of 21" ~ "Problems solved",
           TRUE ~ measure
           )
  )  %>%
  filter(measure_temp == "Problems solved") %>%
  mutate(measure = measure_temp)

## "Unreported" is included here because my best guess is that this study
## used some kind of total problems measure:
## " The creativity tests were administered and scored in
##   standard fashion."

## and combine with individual effect estimates (combined_es())
es_pooled <- pool_es_fixed(es_task, groups, "fixed")
es_combo <- combined_es(es_pooled, es_task, groups)
es_combo %>%
  select(study, measure, measure_orig, h, rl_sm, es_type, N, n, n1, n2, inv_var,
         lower, effect, upper) %>%
  pretty_table(title = "RAT", groupname_col = c("measure", "es_type")) %>%
  # tbl_summary(by = es_type) %>%
  data_color(columns = study,
             colors = scales::col_factor(palette = pal,
                domain = NULL)
            )
```

#### AUT
```{r, echo = F, cache = T}
es_task <- es_individual %>% filter(task == "AUT")
es_pooled <- pool_es_fixed(es_task, groups, "fixed")
es_combo <- combined_es(es_pooled, es_task, groups)
make_measure_es_table(es_combo)
```

#### TTCT-F
```{r, echo = F, cache = T}
es_task <- es_individual %>% filter(task == "TTCT(F)")
es_pooled <- pool_es_fixed(es_task, groups, "fixed")
es_combo <- combined_es(es_pooled, es_task, groups)
make_measure_es_table(es_combo)
```

#### TTCT-V
```{r, echo = F, cache = T}
es_task <- es_individual %>% filter(task == "TTCT(V)")
es_pooled <- pool_es_fixed(es_task, groups, "fixed")
es_combo <- combined_es(es_pooled, es_task, groups)
make_measure_es_table(es_combo)
```
#### Blank (collapse)

