Byrne, B. (1974). Handedness and Musical Ability. British Journal of Psychology, 65(2), 279–281. https://doi.org/10.1111/j.2044-8295.1974.tb01402.x
[[PDF](https://drive.google.com/file/d/1hOW0vQfH7IlvXxVCbbT3axg3nWQ19yVe/view?usp=sharing)]

This study measured the handedness of singers and instrumental musicians, compared to general students ("unselected students").

Handedness was measured using the EHI, and participants were put in three bins: left (less than -50); mixed (between -50 and +50), and right (greater than +50). The present analysis reports a R/L comparison (SR/SL), and a S/M comparison ([SR+SL]/M)

### Calculate frequencies from reported statistics
```{r}
## Calculate the frequency of left, mixed, and right handedness based on percentages in Table 1
#### Singers
n_total <- 134
perc_left <- 5
perc_mixed <- 19
perc_right <- 76
(n_left <- (perc_left*n_total)/100) # 6.7 (7)
(n_mixed <- (perc_mixed*n_total)/100) # 25.46 (25)
(n_right <- (perc_right*n_total)/100) # 101.84 (102)
## Check total
(total <- 7+25+102) # 134 (good)
## R/L (SR/SL)
(n_R <- 102)
(n_L <- 7)
(n_total <- n_R + n_L) # 109
## S/M
(n_S <- 102 + 7) # 109
(n_M <- 25)
(n_total <- n_S + n_M) # 134

#### Instrumental Musicians
n_total <- 108
perc_left <- 3
perc_mixed <- 30.5
perc_right <- 66.5
(n_left <- (perc_left*n_total)/100) # 3.24 (3)
(n_mixed <- (perc_mixed*n_total)/100) # 32.94 (33)
(n_right <- (perc_right*n_total)/100) # 71.82 (72)
## Check total
(total <- 3+33+72) # 108 (good)
## R/L (SR/SL)
(n_R <- 72)
(n_L <- 3)
(n_total <- n_R + n_L) # 75
## S/M
(n_S <- 72 + 3) # 75
(n_M <- 33)
(n_total <- n_S + n_M) # 108

#### General students (controls)
n_total <- 864
perc_left <- 4.5
perc_mixed <- 21.5
perc_right <- 74
(n_left <- (perc_left*n_total)/100) # 38.33 (38)
(n_mixed <- (perc_mixed*n_total)/100) # 185.76 (186)
(n_right <- (perc_right*n_total)/100) # 639.36 (640)
## Check total
(total <- 38+186+640) # 864 (good)
## R/L (SR/SL)
(n_R <- 640)
(n_L <- 38)
(n_total <- n_R + n_L) # 678
## S/M
(n_S <- 640 + 38) # 678
(n_M <- 186)
(n_total <- n_S + n_M) # 864
```

### Load data from input file
```{r}
## Load and display input data
study <- "byrne_1974"
input <- load_input(str_c(study, ".csv"))
pretty_table(input, title = str_c(study, ".csv"))
```

### Calculate effect sizes
```{r, results = "markup"}
es_study <- calculate_es(input, study, OR = T, RR = T, freq = F)
```
```{r}
## Display study results
es_study %>% display_study_es()

## Add study results to full results table
es <- es %>% add_row(es_study)
```

