Giotakos, O. (2004). Handedness and Hobby Preference. Perceptual and Motor Skills, 98(3), 869–872. https://doi.org/10.2466/pms.98.3.869-872 [[PDF](https://drive.google.com/file/d/10cnetxAew8qvOYP8WkHjBFpI20JjLSuN/view?usp=sharing)]

The sample is 879 young men conscripted to the army. 58% strong righties, 3% strong left, 39% mixed. The author reports handedness frequency for those who prefer each of three hobbies: "Reading books, collecting, going to the cinema/theater"; "Art: playing music, drawing, handicraft." "Sports." Here, the frequency of lefties/mixedies preferring "Arts" is compared to the frequency preferring the other two hobbies combined. For R/L, "strong right" is compared to "strong left." For S/M, "strong right" + "strong left" is compared to "mixed."

Handedness measure: AHQ 12 action questionnaire, "strong right" and "strong left" were maximum and minumum scores; everyone else was "mixed."

```{r, include = F}
# ## Calculating frequencies for each comparison
# ## Results will be entered into the input .csv file
# total_n = 879
# ## Arts hobby
# right1 = 94
# mixed1 = 84
# left1 = 6
#
# n1 = right1+mixed1+left1
# n1 # 184
#
# ## Other hobbies
# right2 = 340+74 # 414
# mixed2 = 59+197 # 256
# left2 = 10+15 # 25
#
# n_control = right2+mixed2+left2
# n_control # 695
#
#
# ## R/L (Strong right vs. Mixed + Strong left)
# n_right_creative = right1
# n_left_creative = mixed1 + left1
# n_right_creative # 94
# n_left_creative # 90
# n_right_control = right2
# n_left_control = mixed2 + left2
# n_right_control # 414
# n_left_control # 281
#
#
# ## S/M (Strong right vs. Mixed + Strong Left)
# n_right_creative = right1+left1
# n_left_creative = mixed1
# n_right_creative # 100
# n_left_creative # 84
# n_right_control = right2+left2
# n_left_control = mixed2
# n_right_control # 439
# n_left_control # 256
#
#
# ## R/L (Strong right vs. Strong Left)
# n_creative = right1 + left1
# n_right_creative = right1
# n_left_creative = left1
# n_creative # 100
# n_right_creative # 94
# n_left_creative # 6
# n_control = right2 + left2
# n_right_control = right2
# n_left_control = left2
# n_control #439
# n_right_control # 414
# n_left_control # 25
```

### Load data from input file
```{r}
## Load and display input data
study <- "giotakos_2004"
input <- load_input(str_c(study, ".csv"))
pretty_table(input, title = str_c(study, ".csv"))
```

### Calculate effect sizes
```{r, results = "markup"}
es_study <- calculate_es(input, study, OR = T, RR = T, freq = F)
```
```{r}
## Display study results
es_study %>% display_study_es()

## Add study results to full results table
es <- es %>% add_row(es_study)
```
