Goodman, J. (2014). The wages of sinistrality: Handedness, brain structure, and human capital accumulation. Journal of Economic Perspectives, 28(4), 193–212. https://doi.org/10.1257/jep.28.4.193
[[PDF](https://drive.google.com/file/d/1ea4UDNGawXjiQ9kgjSKCGbdeE0FUaw4g/view?usp=sharing)]

Count are extracted for artists, architects, and musicians from the two US datasets with census occupation codes: the NLSY79 and the NLSY97. (These two datasets comprise the "US dataset" for which Goodman reported lower originality scores for left handers). This extraction is implemented in the script: analyses/professions/0_replicate_goodman/main.Rmd.

Here, odds ratios are extracted for participants in the US dataset with professions in art, architecture, and music.

### Load data from input file (NLSY79)
```{r}
## Load and display input data
study <- "nlsy79"
input <- load_input(str_c(study, ".csv"))
pretty_table(input, title = str_c(study, ".csv"))
```

### Calculate effect sizes
```{r, results = "markup"}
es_study <- calculate_es(input, study, OR = T, RR = T, freq = F)
```
```{r}
## Display study results
es_study %>% display_study_es()

## Add study results to full results table
es <- es %>% add_row(es_study)
```

### Load data from input file (NLSY97)
```{r}
## Load and display input data
study <- "nlsy97"
input <- load_input(str_c(study, ".csv"))
pretty_table(input, title = str_c(study, ".csv"))
```

### Calculate effect sizes
```{r, results = "markup"}
es_study <- calculate_es(input, study, OR = T, RR = T, freq = F)
```
```{r}
## Display study results
es_study %>% display_study_es()

## Add study results to full results table
es <- es %>% add_row(es_study)
```
