Götestam, K. O. (1990). Lefthandedness among students of architecture and music. Perceptual and Motor Skills, 70, 1323–1327.
 [[PDF](https://drive.google.com/file/d/1gTqOsdnZ_ieteXmcj1ENk8zb1PcfKTtE/view?usp=sharing)]

The authors report the frequency of left-handedness among freshman architecture and music students, compared to high school seniors. They calculated handednes from a four item (writing, throwing a ball, threading a needle, and kicking a ball), 3 point scale giving scores from 4 to 12. They defined four handedness categories: "left" (left hand on all items), "left mixed" (always write with left, but do one or more other things with the right hand).

Here, two handedness comparisons are found: R/L (writing hand = left + left mixed vs. right + right mixed), and S/M (right + left / mixed right + mixed left).

```{r, include = F}
# ## Handedness frequencies: calculate and enter in input spreadsheet
#
# #### Architecture (n = 60)
# n <- 60
# right_perc <- 20
# right_mixed_perc <- 68
# left_perc <- 5
# left_mixed_perc <- 7
# (right_n <- (right_perc*n)/100) #12
# (right_mixed_n <- (right_mixed_perc*n)/100) #40.8 (41)
# (left_n <- (left_perc*n)/100) #3
# (left_mixed_n <- (left_mixed_perc*n)/100) #4.2 (4)
# (12 + 41 + 3 + 4)
# ## R/L
# (right_n + right_mixed_n) #52.8 (53)
# (left_n + left_mixed_n) #7.2 (7)
# ## S/M
# (strong <- right_n + left_n) #15
# (mixed <- right_mixed_n + left_mixed_n) #45
#
# #### Music (n = 88)
# n <- 88
# right_perc <- 21.7
# right_mixed_perc <- 63.6
# left_perc <- 4.8
# left_mixed_perc <- 9.9
# (right_n <- (right_perc*n)/100) #19
# (right_mixed_n <- (right_mixed_perc*n)/100) #56
# (left_n <- (left_perc*n)/100) #4.2 (4)
# (left_mixed_n <- (left_mixed_perc*n)/100) #8.7 (9)
# (19 + 56 + 4 + 9)
# ## R/L
# (right_n + right_mixed_n) #75
# (left_n + left_mixed_n) #13
# ## S/M
# (strong <- right_n + left_n) #23
# (mixed <- right_mixed_n + left_mixed_n) #65
#
# #### Control (n = 87)
# n <- 87
# right_perc <- 19.5
# right_mixed_perc <- 64.7
# left_perc <- 1.1
# left_mixed_perc <- 14.7
# (right_n <- (right_perc*n)/100) #17
# (right_mixed_n <- (right_mixed_perc*n)/100) #56
# (left_n <- (left_perc*n)/100) #1
# (left_mixed_n <- (left_mixed_perc*n)/100) #13
# (17 + 56 + 1 + 13)
# ## R/L
# (right_n + right_mixed_n) #73
# (left_n + left_mixed_n) #14
# ## S/M
# (strong <- right_n + left_n) #18
# (mixed <- right_mixed_n + left_mixed_n) #69
```

### Load data from input file
```{r}
## Load and display input data
study <- "gotestam_1990"
input <- load_input(str_c(study, ".csv"))
pretty_table(input, title = str_c(study, ".csv"))
```

### Calculate effect sizes
```{r, results = "markup"}
es_study <- calculate_es(input, study, OR = T, RR = T, freq = F)
```
```{r}
## Display study results
es_study %>% display_study_es()

## Add study results to full results table
es <- es %>% add_row(es_study)
```
