Peterson, J. M. (1979). Left-Handedness: Differences between Student Artists and Scientists. Perceptual and Motor Skills, 48(3), 961–962. https://doi.org/10.2466/pms.1979.48.3.961.
[[PDF](https://drive.google.com/file/d/1of_tWAnFBuXma43i84Pn4lB9ZpE8FtFf/view?usp=sharing)]

The authors report the number and percentage of left handers by major among a group of 1045 undergrads in a psychology course. The majors "Music" and "Design, Arch., Art" can be compared to the majors: Sciences, Behavioral sciences, Business admin, Engineering, and Nursing.

### Load data from input file
```{r}
## Load and display input data
study <- "peterson_1979"
input <- load_input(str_c(study, ".csv"))
pretty_table(input, title = str_c(study, ".csv"))
```

### Calculate effect sizes
```{r, results = "markup"}
es_study <- calculate_es(input, study, OR = T, RR = T, freq = F)
```
```{r}
## Display study results
es_study %>% display_study_es()

## Add study results to full results table
es <- es %>% add_row(es_study)
```
