Preti, A., & Vellante, M. (2007). Creativity and Psychopathology: Higher Rates of Psychosis Proneness and Nonright-Handedness Among Creative Artists Compared to Same Age and Gender Peers. The Journal of Nervous and Mental Disease, 195(10), 837–845. https://doi.org/10.1097/NMD.0b013e3181568180
[[PDF](https://drive.google.com/file/d/1Aa11QXsqRR0e6g13ENfW6VJUplX8Kn8e/view?usp=sharing)]

30 musicians, 25 painters, and 25 writers were compared to 80 controls with noncreative professions.

*"Criteria for inclusion in the index group (herinafter
“artists”) were: to be involved in an artistic profession requir-
ing the production of brand-new, original works, to have been
regularly paid for this activity, to have been exposed to public
judgment of the produced works via an exhibition (for paint-
ers), public execution of musical compositions (for musi-
cians), and publication of books (for writers). A great major-
ity of artists were also carrying on another profession at the
time of the investigation. Most were teachers in their specific
field of expertise; painters were teaching at a local school of
art, musicians taught at a local conservatory, and writers were
often teachers in humanities."*
*Criteria for inclusion in the contrast group (hereinafter
“controls”) were: to be involved in a profession requiring the
repetition of activities that contain no element of innovation;
to have never been paid for a creative work, in any field; to
have never been exposed to public judgment of any creatively
produced work, in any field. Controls were mostly teachers in
the field of humanities or sciences at the local secondary
school or else they were technicians or white collars in a
major national telecom company.*

Handedness was measured continuously with the HPQ, and participants were binned as "strong left", "ambidextrous", or "strong right."

The authors report handedness frequencies for each group, as well as a comparison between mean conitnuous handedness score for the full group of artists and controls.


T-test comparing all artists' handedness to controls':
Controls' laterality score on the HPQ was sensibly lower than among artists:
0.2 (SD = 1.14) versus 1.6 (SD = 3.6), t(158) = 3.41, p = 0.001.

Frequencies by group
Artists (all):
65 right, 10 mixed, 5 left
Controls:
78 right, 2 mixed, 0 left
Writers:
20 right, 5 mixed, 0 left
Musicians:
25 right, 2 mixed, 3 left
Painters:
20 right, 3 mixed, 2 left
Writers + Painters
40 right, 8 mixed, 2 left

Here, writers and painters are binned together.

### Load data from input file
```{r}
## Load and display input data
study <- "preti_2007"
input <- load_input(str_c(study, ".csv"))
pretty_table(input, title = str_c(study, ".csv"))
```

### Calculate effect sizes
```{r, results = "markup"}
es_study <- calculate_es(input, study, OR = T, RR = T, freq = F)
```
```{r}
## Display study results
es_study %>% display_study_es()

## Add study results to full results table
es <- es %>% add_row(es_study)
```
