Schachter, S. C., & Ransil, B. J. (1996). Handedness Distributions in Nine Professional Groups. Perceptual and Motor Skills, 82(1), 51–63. https://doi.org/10.2466/pms.1996.82.1.51
[[PDF](https://drive.google.com/file/d/1ttMj8S-f0RvEhNo_fT1IzTWibT0XhLwC/view?usp=sharing)]

The authors mailed handedness questionnaires that asked EHI questions, and a 3-item question (right, left or ambidextrous).
We can extract (1) mean handedness score for each profession (a R/L comparison), and/or (2) Odds ratios comparing architects to other professions. The odds ratio will be more comparable with other studies.
The authors partition people into Right/Ambidextrous/Left in a few ways:
Table 1: Mean EHI laterality score
Table 2: Frequency for each "global handedness response" (self-reported right, mixed, or left)
Table 3: Frequency and mean EHI score, and "Laterality index" for each global handedness response.
Table 4: EHI cut at 33 (Good R/L comparison).
Table 5: Relative frequencies of EHI laterality scores closest to 50 (right), 30 (mixed), and 10 (left).

The present analysis uses the data from table two, because it enables the calculation of exact odds ratios for both R/L (leaving out mixed handers) and S/M (Strong right and left vs. mixed handers.) The data in table 5 would enable this too, but this partitions the three groups in an unusual way that leaves very few mixed handers.

### Load data from input file
```{r}
## Load and display input data
study <- "schacter_1996"
input <- load_input(str_c(study, ".csv"))
pretty_table(input, title = str_c(study, ".csv"))
```

### Calculate effect sizes
```{r, results = "markup"}
es_study <- calculate_es(input, study, OR = T, RR = T, freq = F)
```
```{r}
## Display study results
es_study %>% display_study_es()

## Add study results to full results table
es <- es %>% add_row(es_study)
```
