Shettel-Neuber, J., & O’Reilly, J. (1983). Handedness and Career Choice: Another Look at Supposed Left/Right Differences. Perceptual and Motor Skills, 57(2), 391–397. https://doi.org/10.2466/pms.1983.57.2.391
[[PDF](https://drive.google.com/file/d/1mULflqu9ckIt6kIX6sxFaLXAzHp9Zyoo/view?usp=sharing)]

The authors report the percentage of faculty in art, architecture, law and psychology who are right, mixed, and left handed. Converting their percentages to frequencies,
Architecture:
22 right, 0 mixed, 1 left (23 total)
Art:
29 right, 1 mixed, 1 left (31 total)
Law:
20 right, 2 mixed, 4 left (26 total)
Psychology:
28 right, 0 mixed, 1 left (29 total)

The present analysis compares Art/Architecture to Law/Psychology (each pairwise), using each possible comparison for R/L, S/M.

### Load data from input file
```{r}
## Load and display input data
study <- "shettel-neuber_1983"
input <- load_input(str_c(study, ".csv"))
pretty_table(input, title = str_c(study, ".csv"))
```

### Calculate effect sizes
```{r, results = "markup"}
es_study <- calculate_es(input, study, OR = T, RR = T, freq = F)
```
```{r}
## Display study results
es_study %>% display_study_es()

## Add study results to full results table
es <- es %>% add_row(es_study)
```
